---
title: "R scripts"
author: "Balami et al. 2025"
format:
  html:
    toc: true
    toc-depth: 3          
    toc-title: "Table of contents"
    number-sections: true
    code-fold: false
    theme: cosmo
    toc-location: left
---


<style>
.fixed-banner {
  position: fixed;
  top: 0;
  left: 0;
  width: 100%;
  background-color: #f8f9fa;
  border-left: 4px solid #2c3e50;
  border-bottom: 1px solid #dee2e6;
  padding: 15px 20px;
  z-index: 1000;
  box-shadow: 0 2px 4px rgba(0,0,0,0.1);
}

body {
  padding-top: 110px !important;
}
</style>

<div class="fixed-banner">
  <h3 style="margin: 0; color: #4c4f52ff; font-size: 1.5em; font-weight: bold; line-height: 1.2;">
    Global meta-analysis reveals a widespread recovery gap in soil fungal communities following vegetation restoration
  </h3>
  
</div>

```{r, echo = FALSE}
# Set the root directory for the knitr/kernel session
# This tells R where to look for files by default
knitr::opts_knit$set(root.dir = '/Users/sujanbalami/Documents/Publications')

```

\newpage

# Load required package

```{r, message = FALSE, warning = FALSE}
library(here)         # File paths
library(shinyDigitise) # Digitize plots
library(clipr)        # Clipboard
library(dplyr)        # Data manipulation
library(metafor)      # Meta-analysis
library(ggplot2)      # Plotting
library(gridExtra)    # Multiple plots
library(tidyverse)    # Data science suite
library(vegan)        # Ecological analysis
library(maps)         # Mapping
library(writexl)      # Excel export
library(forcats)      # Factor handling
```

# Data extraction

## ShinyDigitize

```{r, eval = FALSE}
shinyDigitise("R\\Figure_digisite") # For data extraction from figures

```

## Composition data extraction

```{r, eval = FALSE}
# Read data from clipboard
df<- read_clip_tbl(sep = "\t", header = TRUE, row.names = 1)

# Calculate Euclidean distance matrix
dist_mat<- vegdist(df, method = "euclidean")
dist_matrix<- as.matrix(dist_mat)

# Read group comparisons from clipboard
comparison<- read_clip_tbl(sep = "\t", header = TRUE, row.names = 1)

# Get unique comparison types
comparison_types <- unique(unlist(comparison))

# Calculate WITHIN-group distances
within_distances <- list()
for (type in comparison_types) {
  samples<- rownames(comparison)[comparison[, 1] == type]
  if (length(samples) > 1) {
    sub_dist <- dist_matrix[samples, samples]
    within_distances[[type]] <- sub_dist[upper.tri(sub_dist)]  # Get upper triangle (no duplicates)
  }
}

# Calculate mean and SD for within-group distances
mean_within <- sapply(within_distances, mean)
sd_within   <- sapply(within_distances, sd)

# Calculate BETWEEN-group distances
type_pairs <- combn(comparison_types, 2, simplify = FALSE)  # All possible pairs
between_distances <- list()
for (pair in type_pairs) {
  type1   <- pair[1]
  type2   <- pair[2]
  samples1 <- rownames(comparison)[comparison[, 1] == type1]
  samples2 <- rownames(comparison)[comparison[, 1] == type2]
  between_distances[[paste(type1, type2, sep = "_vs_")]] <-
    as.vector(dist_matrix[samples1, samples2])  # All distances between groups
}

# Calculate mean and SD for between-group distances
mean_between <- sapply(between_distances, mean)
sd_between   <- sapply(between_distances, sd) 

# Compile results
result <- list(
  mean_within_groups = mean_within,
  sd_within_groups   = sd_within,
  mean_between_groups = mean_between,
  sd_between_groups   = sd_between
)
result
```

# Studies distribution

```{r, eval = FALSE}
# Read location data from tab-separated file
location <- read.table("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/location1.txt", 
                       header = TRUE, sep = "\t") 

# Standardize restoration activity labels for better readability
location$Restoration_activity[location$Restoration_activity == "Active"] <- "Active restoration"
location$Restoration_activity[location$Restoration_activity == "Passive"] <- "Natural regeneration"

```

## Restoration strategy maps
```{r, eval = FALSE}
# Load world map data
world_map <- map_data("world")

# Create base world map with light blue oceans
base_plot <- ggplot() +
  borders("world", colour = "transparent", fill = "lightblue") +
  theme(panel.background = element_rect(fill = 'white', 
                                        colour = 'transparent'))
base_plot

# Set map coordinates and customize grid/axes
base_world_with_grid <- base_plot +
  coord_sf(
    crs = 4326,
    xlim = c(-160, 175),
    ylim = c(-55, 80)
  ) +
  scale_x_continuous(breaks = seq(-160, 160, 40)) +
  scale_y_continuous(breaks = seq(-40, 80, 20)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),  # Remove x-axis tick labels
    axis.text.y = element_blank(),  # Remove y-axis tick labels
    axis.ticks = element_blank()    # Remove axis ticks
  ) +
  labs(x = NULL, y = NULL)

print(base_world_with_grid)

# Set factor levels for ecosystems and disturbance types
location$Ecosystem <- factor(location$Ecosystem, levels = c("Grassland", "Shrubland", "Forest", "Desert"))
location$Past_disturbance_type <- factor(location$Past_disturbance_type, levels = c("Agriculture", 
                                                                                    "Pasture", 
                                                                                    "Mining", 
                                                                                    "Deforestation",
                                                                                   "Erosion",
                                                                                   "Monoculture plantation",
                                                                                   "Others"))

# Create final map with points colored by disturbance and shaped by ecosystem
map_with_points <- base_world_with_grid +
  geom_point(data = location,  
             aes(x = Longitude, y = Latitude, fill = Past_disturbance_type, shape = Ecosystem),
             size = 1, alpha = 0.5,
             color = "black",
             stroke = 0.3) +
  scale_fill_manual(
    values = c(
      "Agriculture" = "red",
      "Pasture" = "blue", 
      "Mining" = "darkgreen", 
      "Deforestation" = "orange", 
      "Erosion" = "brown", 
      "Monoculture plantation" = "cyan", 
      "Others" = "yellow"
    )
  ) +
  scale_shape_manual(
    values = c(
      "Grassland" = 21,
      "Shrubland" = 24,
      "Forest" = 22,
      "Desert" = 23
    )
  ) +
  labs(fill = "Past disturbance", shape = "Ecosystem", x = NULL, y = NULL) +
  theme_bw() +
  theme(
      legend.title = element_text(size = 10),
    legend.position = "right",
    legend.text = element_text(size = 8),  # Reduced legend text size
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    strip.text = element_blank(),
    panel.border = element_blank(),
    panel.grid.major = element_blank()
  ) +
  facet_wrap(~ Restoration_activity, nrow = 2) +  # Split by restoration type
  guides(
    fill = guide_legend(
      override.aes = list(shape = 21, color = "black", size = 2.5),
      keyheight = unit(0.3, "cm"),
      keywidth = unit(0.8, "cm"),
      default.unit = "cm"
    ),
    shape = guide_legend(
      override.aes = list(fill = "black", color = "black", size = 2.5),
      keyheight = unit(0.3, "cm"),  
      keywidth = unit(0.8, "cm"),
      default.unit = "cm"
    )
  )

print(map_with_points)

```

## Restoration time map
```{r, eval = FALSE}

# Set factor levels for restoration time groups
location_time$Group <- factor(location_time$Group, levels = c("recent", "short-term", "long-term", "seminatural"))

# Create map with bubble sizes proportional to restoration time
map_with_points2 <- base_world_with_grid +
  geom_point(data = location_time,  
             aes(x = Longitude, y = Latitude, size = Restoration_time),
             shape = 21,       
             color = "black",
             stroke = 0.1) +
  scale_size_continuous(
    name = "Restoration time (Yrs)",
    range = c(0.5, 5),  # Min and max bubble sizes
    breaks = c(10, 20, 30, 50, 100),
    labels = c("10", "20", "30", "50", "100")
  ) +
  labs(y = NULL, x = NULL) +
  facet_wrap(~ Group, nrow = 4, ncol = 1) +  # Vertical facet layout
  theme_bw() +
  theme(
    legend.title = element_text(size = 8),
    legend.position = "right",
    legend.text = element_text(size = 6),
    panel.grid.major = element_blank(),
    strip.text = element_blank(),  # Remove facet labels
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank()
  ) 

print(map_with_points2)

# Save high-resolution TIFF for publication
ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/Restoration_time_maps.tiff", 
       plot =  map_with_points2, dpi = 600, height = 5, width = 7)

```

## Data overview number of studies

```{r, eval = FALSE}
# Read data overview CSV file
data_overview <- read.csv("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/data_overview.csv", 
                          header = TRUE)

# Reorder Types by number of Studies within each Overview category
data_overview_ordered <- data_overview %>%
  group_by(Overview) %>%
  mutate(Types = fct_reorder(Types, Studies)) %>%  # Order bars by study count
  ungroup()

# Convert to factors for proper plotting
data_overview_ordered$Overview <- as.factor(data_overview_ordered$Overview)
data_overview_ordered$Types <- as.factor(data_overview_ordered$Types)

# Split data into three categories for separate plots/analysis
restoration_strategy_overview <- data_overview_ordered[
    data_overview_ordered$Overview == "Restoration strategy",]
past_disturbance_overview <- data_overview_ordered[
    data_overview_ordered$Overview == "Past disturbance",]
ecosystem_overview <- data_overview_ordered[
    data_overview_ordered$Overview == "Ecosystem",]

```

## Figure 1

```{r, eval = FALSE}
# Create horizontal bar plot for restoration strategy overview
restoration_strategy_overview_plot <- ggplot(
    restoration_strategy_overview, 
    aes(x = Studies, y = forcats::fct_reorder(Types, Studies))) +
  geom_bar(stat = "identity", alpha = 0.8, fill = "grey90", width = 0.5) +
  geom_text(aes(label = Studies), hjust = -0.1, size = 3.5) +  # Add count labels
  labs(title = "Restoration strategy",
       x = NULL,
       y = NULL) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain", size = 10),
    axis.text.x = element_blank(),
    axis.title.y = element_text(size = 10, vjust = 0),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line.y = element_line(linewidth = 0.1, color = "grey50"),
    axis.line.x = element_line(linewidth = 0.1, color = "grey50"),
    axis.ticks.x = element_line(linewidth = 0.1, color = "grey50"),
    plot.margin = margin(t = 10, r = 10, b = 80, l = 10, unit = "pt")
  ) + 
  scale_x_continuous(expand = expansion(mult = c(0, 0.2)), position = "top")  # Add space for labels

restoration_strategy_overview_plot

# Create horizontal bar plot for past disturbance overview
distrubance_overview_plot <- ggplot(
    past_disturbance_overview, 
    aes(x = Studies, y = forcats::fct_reorder(Types, Studies))) +
  geom_bar(stat = "identity", alpha = 0.8, fill = "grey90", width = 0.5) +
  geom_text(aes(label = Studies), hjust = -0.1, size = 3.5) +
  labs(title = "Past distrubance",
       x = NULL,
       y = NULL) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain", size = 10),
    axis.title.y = element_text(size = 10, vjust = 0), 
    axis.text.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line.y = element_line(linewidth = 0.1, color = "grey50"),
    axis.line.x = element_line(linewidth = 0.1, color = "grey50"),
    axis.ticks.x = element_line(linewidth = 0.1, color = "grey50"))+ 
  scale_x_continuous(expand = expansion(mult = c(0, 0.2)), position = "top") 
distrubance_overview_plot

# Create horizontal bar plot for ecosystem overview
ecosystem_overview_plot <- ggplot(
    ecosystem_overview, aes(x = Studies, 
                            y = forcats::fct_reorder(Types, Studies))) +
  geom_bar(stat = "identity", alpha = 0.8, fill = "grey90", width = 0.5) +
  geom_text(aes(label = Studies), hjust = -0.1, size = 3.5) +
  labs(title = "Ecosystem",
       x = NULL,
       y = NULL) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain", size = 10),
    axis.title.x = element_text(size = 10, vjust = 0),
    axis.text.y = element_text(size = 10),
    axis.text.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.line.y = element_line(linewidth = 0.1, color = "grey50"),
    axis.line.x = element_line(linewidth = 0.1, color = "grey50"),
    axis.ticks.x = element_line(linewidth = 0.1, color = "grey50"),
    plot.margin = margin(t = 10, r = 10, b = 40, l = 10, unit = "pt")
  ) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.2)), position = "top") 

# Arrange the three overview plots side by side
library(gridExtra)
plot_overview <- grid.arrange(
  ecosystem_overview_plot, 
  distrubance_overview_plot,
  restoration_strategy_overview_plot, 
  ncol = 3
)

# Combine map with overview plots (map on top, bar charts below)
plot_overview_map <- grid.arrange(
  map_with_points,  
  plot_overview, 
  nrow = 2,
  heights = c(3, 1)  # Map takes 3/4 space, bar charts 1/4
)

# Save combined figure as high-resolution TIFF
ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/Figure_1.tiff", 
       plot =  plot_overview_map, dpi = 600, height = 8, width = 8.5)
```

## Data overview restoration strategies
```{r, eval = FALSE}
# Read restoration comparison data
data_overview_restoration <- read.csv("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/restoration_comparison.csv", 
                          header = TRUE)

# Set factor levels for consistent ordering
data_overview_restoration$Metrics <- factor(data_overview_restoration$Metrics, 
                                 levels = c("Observed richness",
                                            "Chao1 richness",
                                            "Shannon index",
                                            "Simpson index",
                                            "Ascomycota",
                                            "Basidiomycota",
                                            "Composition",
                                           "PLFA content"))

data_overview_restoration$Restoration_activity <- factor(data_overview_restoration$Restoration_activity, 
                                 levels = c("Active restoration",
                                            "Natural regeneration"))

# Set threshold for breaking lines when values are too high
break_threshold <- 50 

# Prepare data for broken bar segments
data_segmented_restoration <- data_overview_restoration %>% 
  mutate(
    needs_break = Comparison > break_threshold,
    segment_end = ifelse(needs_break, break_threshold * 0.9, Comparison)
  )

# Calculate positions with proper spacing
max_metrics <- max(as.numeric(factor(data_segmented_restoration$Metrics)))
spacing_multiplier <- 3

# Create spread out x-positions for metrics
data_segmented_restoration <- data_segmented_restoration %>%
  mutate(
    x_position = (as.numeric(factor(Metrics)) - 1) * spacing_multiplier + 1
  )

# Calculate plot limits
min_x <- min(data_segmented_restoration$x_position) - 1
max_x <- max(data_segmented_restoration$x_position) + 1
center_x <- (min_x + max_x) / 2  # Center point for line origins

# Create lollipop plot with broken segments for high values
overview_restoration <- ggplot(data_segmented_restoration, aes(x = center_x, y = 0)) +
  # First segment (for all lines)
  geom_segment(aes(xend = x_position, yend = segment_end, color = Metrics),
               size = 1, lineend = "round") +
  # Second segment (only for broken lines) - make it shorter and leveled
  geom_segment(data = subset(data_segmented_restoration, needs_break == TRUE),
               aes(x = x_position, 
                   xend = x_position,
                   y = break_threshold * 1.1, 
                   yend = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3,  # Shorter segment
                   color = Metrics),
               size = 1, lineend = "round") +
  geom_hline(yintercept = 0, color = "black", size = 0.2) +
  # Add break indicator
  geom_point(data = subset(data_segmented_restoration, needs_break == TRUE),
             aes(x = x_position, y = break_threshold),
             shape = 21, fill = "white", color = "transparent", size = 2) +
  # Data labels - adjust position for shorter segments
  geom_text(data = subset(data_segmented_restoration, needs_break == TRUE),
            aes(x = x_position, 
                y = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3,  # Match segment end
                label = Comparison),
            vjust = -0.8, size = 2.5) +
  # Data labels for non-broken lines
  geom_text(data = subset(data_segmented_restoration, !needs_break),
            aes(x = x_position, y = Comparison, label = Comparison),
            vjust = -0.8, size = 2.5) +
  facet_wrap(~ Restoration_activity, nrow = 1, switch = "x") +
  labs(x = NULL, y = NULL, color = NULL) +
  scale_color_manual(
    values = c(
      "Observed richness" = "darkgreen",
      "Chao1 richness" = "limegreen", 
      "Shannon index" = "springgreen",
      "Simpson index" = "cyan3",
      "Ascomycota" = "orange",
      "Basidiomycota" = "brown",
      "Composition" = "steelblue",
      "PLFA content" = "grey60"
    )
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
      legend.text = element_text(size = 6),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(color = "black"),
    panel.spacing.x = unit(0.2, "cm"),
    panel.spacing.y = unit(-0.5, "cm"),
    plot.margin = margin(0, 0, 0, 0, "pt")
  ) +
  coord_cartesian(xlim = c(min_x, max_x), 
                  ylim = c(0, max(data_segmented_ecosystem$Comparison) * 0.6))

overview_restoration

```

## Data overview ecosystem types
```{r, eval = FALSE}
data_overview <- read.csv("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/forest_comparison.csv", 
                          header = TRUE)

data_overview$Metrics <- factor(data_overview$Metrics, 
                                 levels = c("Observed richness",
                                            "Chao1 richness",
                                            "Shannon index",
                                            "Simpson index",
                                            "Ascomycota",
                                            "Basidiomycota",
                                            "Composition",
                                           "PLFA content"))

data_overview$Ecosystem <- factor(data_overview$Ecosystem, 
                                 levels = c("Forest",
                                            "Grassland",
                                            "Shrubland",
                                            "Desert"))


# Use the correct dataset name
break_threshold <- 50  # Adjust based on your data range

data_segmented_ecosystem <- data_overview %>%  # Use the correct dataset
  mutate(
    needs_break = Comparison > break_threshold,
    segment_end = ifelse(needs_break, break_threshold * 0.9, Comparison)
  )

# Calculate positions with proper spacing
max_metrics <- max(as.numeric(factor(data_segmented_ecosystem$Metrics)))
spacing_multiplier <- 3

# Create more spread out x-positions
data_segmented_ecosystem <- data_segmented_ecosystem %>%
  mutate(
    x_position = (as.numeric(factor(Metrics)) - 1) * spacing_multiplier + 1
  )

# Calculate automatic limits based on the actual data
min_x <- min(data_segmented_ecosystem$x_position) - 1
max_x <- max(data_segmented_ecosystem$x_position) + 1
center_x <- (min_x + max_x) / 2  # Calculate center based on actual positions

overview_ecosystem <- ggplot(data_segmented_ecosystem, aes(x = center_x, y = 0)) +
  # First segment (for all lines)
  geom_segment(aes(xend = x_position, yend = segment_end, color = Metrics),
               size = 1, lineend = "round") +
  # Second segment (only for broken lines) - make it shorter and leveled
  geom_segment(data = subset(data_segmented_ecosystem, needs_break == TRUE),
               aes(x = x_position, 
                   xend = x_position,
                   y = break_threshold * 1.1, 
                   yend = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3,  # Shorter segment
                   color = Metrics),
               size = 1, lineend = "round") +
  geom_hline(yintercept = 0, color = "black", size = 0.2) +
  # Add break indicator
  geom_point(data = subset(data_segmented_ecosystem, needs_break == TRUE),
             aes(x = x_position, y = break_threshold),
             shape = 21, fill = "white", color = "transparent", size = 2) +
  # Data labels - adjust position for shorter segments
  geom_text(data = subset(data_segmented_ecosystem, needs_break == TRUE),
            aes(x = x_position, 
                y = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3,  # Match segment end
                label = Comparison),
            vjust = -0.8, size = 2.5) +
  # Data labels for non-broken lines
  geom_text(data = subset(data_segmented_ecosystem, !needs_break),
            aes(x = x_position, y = Comparison, label = Comparison),
            vjust = -0.8, size = 2.5) +
  facet_wrap(~ Ecosystem, nrow = 1, switch = "x") +
  labs(x = NULL, y = NULL, color = NULL) +
  scale_color_manual(
    values = c(
      "Observed richness" = "darkgreen",
      "Chao1 richness" = "limegreen", 
      "Shannon index" = "springgreen",
      "Simpson index" = "cyan3",
      "Ascomycota" = "orange",
      "Basidiomycota" = "brown",
      "Composition" = "steelblue",
      "PLFA content" = "grey60"
    )
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
      legend.text = element_text(size = 6),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(color = "black"),
    panel.spacing.x = unit(0.2, "cm"),
    panel.spacing.y = unit(-0.5, "cm"),
    plot.margin = margin(0, 0, 0, 0, "pt")
  ) +
  coord_cartesian(xlim = c(min_x, max_x), 
                  ylim = c(0, max(data_segmented_ecosystem$Comparison) * 0.6))

overview_ecosystem

```

## Data overview past disturbance types
```{r, eval = FALSE}
data_overview_past_disturbance <- read.csv("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/past_disturbance.csv", 
                          header = TRUE)

data_overview_past_disturbance$Metrics <- factor(data_overview_past_disturbance$Metrics, 
                                 levels = c("Observed richness",
                                            "Chao1 richness",
                                            "Shannon index",
                                            "Simpson index",
                                            "Ascomycota",
                                            "Basidiomycota",
                                            "Composition",
                                           "PLFA content"))

data_overview_past_disturbance$Past_disturbance <- factor(data_overview_past_disturbance$Past_disturbance, 
                                 levels = c("Agriculture",
                                            "Deforestation",
                                            "Erosion",
                                            "Mining",
                                           "Monoculture plantation",
                                           "Pasture",
                                           "Others"))

# Use the correct dataset name
break_threshold <- 50  # Adjust based on your data range

data_segmented_past_disturbance <- data_overview_past_disturbance %>%  # Use the correct dataset
  mutate(
    needs_break = Comparison > break_threshold,
    segment_end = ifelse(needs_break, break_threshold * 0.9, Comparison)
  )

# Calculate positions with proper spacing
max_metrics <- max(as.numeric(factor(data_segmented$Metrics)))
spacing_multiplier <- 3

# Create more spread out x-positions
data_segmented_past_disturbance <- data_segmented_past_disturbance %>%
  mutate(
    x_position = (as.numeric(factor(Metrics)) - 1) * spacing_multiplier + 1
  )

# Calculate automatic limits based on the actual data
min_x <- min(data_segmented_past_disturbance$x_position) - 1
max_x <- max(data_segmented_past_disturbance$x_position) + 1
center_x <- (min_x + max_x) / 2  # Calculate center based on actual positions

overview_past_disturbance <- ggplot(data_segmented_past_disturbance, aes(x = center_x, y = 0)) +
  # First segment (for all lines)
  geom_segment(aes(xend = x_position, yend = segment_end, color = Metrics),
               size = 1, lineend = "round") +
  # Second segment (only for broken lines) - make it shorter and leveled
  geom_segment(data = subset(data_segmented_past_disturbance, needs_break == TRUE),
               aes(x = x_position, 
                   xend = x_position,
                   y = break_threshold * 1.1, 
                   yend = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3,  # Shorter segment
                   color = Metrics),
               size = 1, lineend = "round") +
geom_hline(yintercept = 0, color = "black", size = 0.2)+
  # Add break indicator
  geom_point(data = subset(data_segmented_past_disturbance, needs_break == TRUE),
             aes(x = x_position, y = break_threshold),
             shape = 21, fill = "white", color = "transparent", size = 2) +
  # Data labels - adjust position for shorter segments
  geom_text(data = subset(data_segmented_past_disturbance, needs_break == TRUE),
            aes(x = x_position, 
                y = break_threshold * 1.1 + (Comparison - break_threshold) * 0.3,  # Match segment end
                label = Comparison),
            vjust = -0.8, size = 2.5) +
  # Data labels for non-broken lines
  geom_text(data = subset(data_segmented_past_disturbance, !needs_break),
            aes(x = x_position, y = Comparison, label = Comparison),
            vjust = -0.8, size = 2.5) +
  facet_wrap(~ Past_disturbance, nrow = 1, switch = "x") +
  labs(x = NULL, y = NULL, color = NULL) +
  scale_color_manual(
    values = c(
      "Observed richness" = "darkgreen",
      "Chao1 richness" = "limegreen", 
      "Shannon index" = "springgreen",
      "Simpson index" = "cyan3",
      "Ascomycota" = "orange",
      "Basidiomycota" = "brown",
      "Composition" = "steelblue",
      "PLFA content" = "grey60"
    )
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
      legend.text = element_text(size = 8),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(color = "black"),
    panel.spacing.x = unit(0.2, "cm"),
      panel.spacing.y = unit(-0.5, "cm"),
    plot.margin = margin(0, 0, 0, 0, "pt")
  ) +
  coord_cartesian(xlim = c(min_x, max_x), 
                  ylim = c(0, max(data_segmented_past_disturbance$Comparison) * 1))

overview_past_disturbance

```

## Figure S2
```{r, eval = FALSE}
# Combine restoration and ecosystem overview plots side by side
combined_plot1 <- grid.arrange(overview_restoration, overview_ecosystem, nrow = 1,
                              widths = c(0.6, 1))  # Restoration takes 60%, ecosystem 100% width
combined_plot1

# Add past disturbance overview below the first combination
combined_plot2 <- grid.arrange(combined_plot1, overview_past_disturbance, nrow = 2)
combined_plot2

# Save the final combined overview figure
ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/overview.tiff", 
       plot =  combined_plot2, dpi = 600, height = 6, width = 9)

```

## Figure S4
```{r, eval = FALSE}
location_time <- read.table("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/location_restoration_time.txt", 
                       header = TRUE, sep = "\t") 

location_time$Group <- factor(location_time$Group, levels = c("< 10 years", "10 to 20 years", "20 to 30 years", "30 to 40 years", "> 40 years"))                       

bar_plot <- location_time %>%
  count(Group) %>%
  ggplot(aes(x = Group, y = n)) +
  geom_col(color = "black", linewidth = 0.25, fill = "grey80", width = 0.7) +
  geom_text(aes(label = n), vjust = -0.5, size = 3.5, fontface = "plain") + # Add count labels
  labs(
    y = "Number of studies",
    x = "Restoration time"
  ) +
  theme_bw() +
  theme(
    # Remove title for publication (titles go in figure captions)
    plot.title = element_blank(),
    
    # Axis labels
    axis.title = element_text(size = 12, face = "plain", color = "black"),
    axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
    axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
    
    # Axis text
    axis.text = element_text(size = 10, color = "black"),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    
    # Grid and panel
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", linewidth = 0.5),
    
    # Plot margins
    plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
    
    # Remove legend
    legend.position = "none"
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) # Remove space below 0, add 10% above

print(bar_plot)

ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/map/Figure_S3.tiff", plot =  bar_plot, dpi = 600, height = 6, width = 5) 
```

# Import data

## Alpha diversity

```{r, eval = FALSE}
alpha_resVsdeg <- read.csv(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/alpha_resVsdeg.csv", 
                           header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, 
             Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time)
  )
alpha_resVsref <- read.csv(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/alpha_resVsref.csv", 
                           header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, 
             Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time)  
  )
OTU_resVsdeg <- alpha_resVsdeg[1:191,]
Chao_resVsdeg <- alpha_resVsdeg[192:407,]
Shannon_resVsdeg <- alpha_resVsdeg[408:709,]
Simpson_resVsdeg <- alpha_resVsdeg[710:799,]
OTU_resVsref <- alpha_resVsref[1:79,]
Chao_resVsref <- alpha_resVsref[80:154,]
Shannon_resVsref <- alpha_resVsref[155:289,]
Simpson_resVsref <- alpha_resVsref[290:341,]
```

## Composition

```{r, eval = FALSE}
beta <- read.csv("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/beta.csv", 
                 header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, 
             Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time)  
  )
structure <- read.csv(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/composition.csv", 
    header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, 
             Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time)  
  )
beta_diversity_degraded <- beta %>% filter(
    Comparison == "Restored vs Degraded")
beta_diversity_reference <- beta %>% filter(
    Comparison == "Restored vs Reference")
structure_degraded <- structure %>% filter(
    Comparison == "Restored vs Degraded")
structure_reference <- structure %>% filter(
    Comparison == "Restored vs Reference")
composition_raw_degraded <- bind_rows(beta_diversity_degraded,
                                      structure_degraded)
composition_raw_reference <- bind_rows(beta_diversity_reference,
                                       structure_reference)
```

## Relative abundance

```{r, eval = FALSE}
Ascomycota_deg <- read.csv(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/ascomycota_resVsdeg.csv", 
                           header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, 
             Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time)  
  )
Ascomycota_ref <- read.csv(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/ascomycota_resVsref.csv", 
                           header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, 
             Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time)  
  )
Basidiomycota_deg <- read.csv(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/basidiomycota_resVsdeg.csv", 
                              header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time)  
  ) 
Basidiomycota_ref <- read.csv(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/basidiomycota_resVsref.csv", 
                              header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, 
             Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time)  
  )
abundance_raw_degraded <- bind_rows(Ascomycota_deg, 
                                    Basidiomycota_deg)
abundance_raw_reference <- bind_rows(Ascomycota_ref, 
                                     Basidiomycota_ref)
```

## Biomass

```{r}
PLFA_degraded <- read.csv(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/plfa_resVsdeg.csv", 
                          header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, 
             Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time)  
  )
PLFA_reference <- read.csv(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/working_data/plfa_resVsref.csv", 
                           header = TRUE) %>% 
  mutate(
    across(c(ID, 
             Restoration_strategy, 
             Ecosystem, 
             Past_disturbance_type), as.factor),
    Restoration_time = as.numeric(Restoration_time))  
```

# Response ratio

```{r, eval = FALSE}
calculate_resVsdeg <- function(data, n1i, n2i, m1i, m2i, sd1i, sd2i) {
  escalc(measure = "ROM", 
         n1i = Restored_SS, n2i = Degraded_SS,
         m1i = Restored_Mean, m2i = Degraded_Mean,
         sd1i = Restored_SD, sd2i = Degraded_SD,
         data = data, append = TRUE)
}
calculate_resVsref <- function(data, n1i, n2i, m1i, m2i, sd1i, sd2i) {
  escalc(measure = "ROM", 
         n1i = Restored_SS, n2i = Reference_SS,
         m1i = Restored_Mean, m2i = Reference_Mean,
         sd1i = Restored_SD, sd2i = Reference_SD,
         data = data, append = TRUE)
}
```

## Alpha diversity

```{r, eval = FALSE}
a_OTU_resVsdeg <- calculate_resVsdeg(OTU_resVsdeg, Restored_SS, Degraded_SS,
                                     Restored_Mean, Degraded_Mean, 
                                     Restored_SD, Degraded_SD)
a_Chao_resVsdeg <- calculate_resVsdeg(Chao_resVsdeg, Restored_SS, Degraded_SS, 
                                      Restored_Mean, Degraded_Mean, 
                                      Restored_SD, Degraded_SD)
a_Shannon_resVsdeg <- calculate_resVsdeg(Shannon_resVsdeg, Restored_SS, 
                                         Degraded_SS, Restored_Mean, 
                                         Degraded_Mean, Restored_SD, 
                                         Degraded_SD)
a_Simpson_resVsdeg <- calculate_resVsdeg(Simpson_resVsdeg, Restored_SS, 
                                         Degraded_SS, Restored_Mean, 
                                         Degraded_Mean, Restored_SD, 
                                         Degraded_SD)
a_OTU_resVsref <- calculate_resVsref(OTU_resVsref, Restored_SS, 
                                     Reference_SS, Restored_Mean, 
                                     Reference_Mean, Restored_SD, 
                                     Reference_SD)
a_Chao_resVsref <- calculate_resVsref(Chao_resVsref, Restored_SS, 
                                      Reference_SS, Restored_Mean, 
                                      Reference_Mean, Restored_SD, 
                                      Reference_SD)
a_Shannon_resVsref <- calculate_resVsref(Shannon_resVsref, Restored_SS, 
                                         Reference_SS, Restored_Mean, 
                                         Reference_Mean, Restored_SD, 
                                         Reference_SD)
a_Simpson_resVsref <- calculate_resVsref(Simpson_resVsref, Restored_SS, 
                                         Reference_SS, Restored_Mean, 
                                         Reference_Mean, Restored_SD, 
                                         Reference_SD)
a_OTU_resVsdeg <- a_OTU_resVsdeg[-c(6, 7, 17, 18, 19, 111, 168, 172), ] # Filter some extreme lnRR
a_Chao_resVsdeg <- a_Chao_resVsdeg[-c(21, 25, 27, 98, 151, 203), ]
a_Shannon_resVsdeg <- a_Shannon_resVsdeg[-c(1, 2, 3, 124, 202), ]
alpha_diversity_deg_raw <- rbind(a_OTU_resVsdeg, a_Chao_resVsdeg,a_Shannon_resVsdeg, a_Simpson_resVsdeg )
alpha_diversity_ref_raw <- rbind(a_OTU_resVsref, a_Chao_resVsref,a_Shannon_resVsref, a_Simpson_resVsref )
```

## Composition

```{r, eval = FALSE}
# Composition data already have lnRR and variance (vi)
```

## Relative abundance

```{r, eval = FALSE}
a_Ascomycota_degraded <- calculate_resVsdeg(Ascomycota_deg, Restored_SS, 
                                            Degraded_SS, Restored_Mean, 
                                            Degraded_Mean, Restored_SD, 
                                            Degraded_SD)
a_Ascomycota_reference <- calculate_resVsref(Ascomycota_ref, Restored_SS, 
                                             Degraded_SS, Restored_Mean, 
                                             Degraded_Mean, Restored_SD, 
                                             Degraded_SD)
a_Basidiomycota_degraded <- calculate_resVsdeg(Basidiomycota_deg, Restored_SS, 
                                               Degraded_SS, Restored_Mean, 
                                               Degraded_Mean, Restored_SD, 
                                               Degraded_SD)
a_Basidiomycota_reference <- calculate_resVsref(Basidiomycota_ref, 
                                                Restored_SS, Degraded_SS, 
                                                Restored_Mean, Degraded_Mean, 
                                                Restored_SD, Degraded_SD)
Ascomycota_Basidiomycota_deg_raw <- rbind(a_Ascomycota_degraded, 
                                          a_Basidiomycota_degraded)
Ascomycota_Basidiomycota_ref_raw <- rbind(a_Ascomycota_reference, 
                                          a_Basidiomycota_reference)
```

## Biomass

```{r, eval = FALSE}
a_PLFA_degraded <- calculate_resVsdeg(PLFA_degraded, Restored_SS, Degraded_SS, 
                                      Restored_Mean, Degraded_Mean, 
                                      Restored_SD, Degraded_SD)
a_PLFA_reference <- calculate_resVsref(PLFA_reference, Restored_SS, 
                                       Degraded_SS, Restored_Mean, 
                                       Degraded_Mean, Restored_SD, Degraded_SD)
```

# Publication bias

## Egger's test

### Alpha diversity

```{r, eval = FALSE}
eggers_OTU_deg <- rma(yi = yi, vi = vi, data = a_OTU_resVsdeg, 
                      method = "REML")
regtest(eggers_OTU_deg)
eggers_OTU_ref <- rma(yi = yi, vi = vi, data = a_OTU_resVsref, 
                      method = "REML")
regtest(eggers_OTU_ref)
eggers_Chao_deg <- rma(yi = yi, vi = vi, data = a_Chao_resVsdeg, 
                       method = "REML")
regtest(eggers_Chao_deg)
eggers_Chao_ref <- rma(yi = yi, vi = vi, data = a_Chao_resVsref, 
                       method = "REML")
regtest(eggers_Chao_ref)
eggers_Shannon_deg <- rma(yi = yi, vi = vi, data = a_Shannon_resVsdeg, 
                          method = "REML")
regtest(eggers_Shannon_deg)
eggers_Shannon_ref <- rma(yi = yi, vi = vi, data = a_Shannon_resVsref, 
                          method = "REML")
regtest(eggers_Shannon_ref)
eggers_Simpson_deg <- rma(yi = yi, vi = vi, data = a_Simpson_resVsdeg, 
                          method = "REML")
regtest(eggers_Simpson_deg)
eggers_Simpson_ref <- rma(yi = yi, vi = vi, data = a_Simpson_resVsref, 
                          method = "REML")
regtest(eggers_Simpson_ref)
```

### Composition

```{r, eval = FALSE}
eggers_beta_diversity_degraded <- rma(yi = yi, vi = vi, 
                                      data = beta_diversity_degraded, 
                                      method = "REML")
regtest(eggers_beta_diversity_degraded)
eggers_beta_diversity_reference <- rma(yi = yi, vi = vi, 
                                       data = beta_diversity_reference, 
                                       method = "REML")
regtest(eggers_beta_diversity_reference)
eggers_structure_degraded <- rma(yi = yi, vi = vi, 
                                 data = structure_degraded, 
                                 method = "REML")
regtest(eggers_structure_degraded)
eggers_structure_reference <- rma(yi = yi, vi = vi, 
                                  data = structure_reference, 
                                  method = "REML")
regtest(eggers_structure_reference)
```

### Relative abundance

```{r, eval = FALSE}
eggers_Ascomycota_deg <- rma(yi = yi, vi = vi, 
                             data = a_Ascomycota_degraded, 
                             method = "REML")
regtest(eggers_Ascomycota_deg)
eggers_Ascomycota_ref <- rma(yi = yi, vi = vi, 
                             data = a_Ascomycota_reference, 
                             method = "REML")
regtest(eggers_Ascomycota_ref)
eggers_Basidiomycota_deg <- rma(yi = yi, vi = vi, 
                                data = a_Basidiomycota_degraded, 
                                method = "REML")
regtest(eggers_Basidiomycota_deg)
eggers_Basidiomycota_ref <- rma(yi = yi, vi = vi, 
                                data = a_Basidiomycota_reference, 
                                method = "REML")
regtest(eggers_Basidiomycota_ref)
```

### Biomass

```{r, eval = FALSE}
eggers_PLFA_deg <- rma(yi = yi, vi = vi, 
                       data = a_PLFA_degraded, 
                       method = "REML")
regtest(eggers_PLFA_deg)
eggers_PLFA_ref <- rma(yi = yi, vi = vi, 
                       data = a_PLFA_reference, 
                       method = "REML")
regtest(eggers_PLFA_deg)
```

## Funnel plot

### Funnel plot alpha diversity

```{r, eval = FALSE}
png(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/funnel_plot/funnel_plot1.tiff", 
    width = 10, height = 6, units = "in", res = 300)
# Set larger margins for multi-plot layout
par(mfrow = c(2, 4), mar = c(4.5, 4.5, 4, 2), mgp = c(3, 1, 0))
    
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_OTU_resVsdeg), 
       main = "Observed richness \n(Restored vs Degraded)", 
       xlab = "Effect Size (lnRR)", ylab = "SE",
       pch = 21, bg = rgb(1, 0.5, 0, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_OTU_resVsref), 
       main = "Observed richness \n(Restored vs Reference)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Chao_resVsdeg), 
       main = "Chao1 richness \n(Restored vs Degraded)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(1, 0.5, 0, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white",
      mar = c(4.5, 4.5, 4, 2))
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Chao_resVsref), 
       main = "Chao1 richness \n(Restored vs Reference)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Shannon_resVsdeg), 
       main = "Shannon index \n(Restored vs Degraded)", 
       xlab = "Effect Size (lnRR)", ylab = "SE",
       pch = 21, bg = rgb(1, 0.5, 0, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white",
      mar = c(4.5, 4.5, 4, 2))
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Shannon_resVsref), 
       main = "Shannon index \n(Restored vs Reference)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Simpson_resVsdeg), 
       main = "Simpson index \n(Restored vs Degraded)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(1, 0.5, 0, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Simpson_resVsref), 
       main = "Simpson index \n(Restored vs Reference)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
dev.off()
```

### Funnel plot relative abundance

```{r, eval = FALSE}
png(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/funnel_plot/funnel_plot2.tiff", 
    width = 10, height = 3, units = "in", res = 300)
# Set larger margins for multi-plot layout
par(mfrow = c(1, 4), mar = c(4.5, 4.5, 4, 2), mgp = c(3, 1, 0))
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Ascomycota_degraded), 
       main = "Ascomycota \n(Restored vs Degraded)", 
       xlab = "Effect Size (lnRR)", ylab = "SE",
       pch = 21, bg = rgb(1, 0.5, 0, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Ascomycota_reference), 
       main = "Ascomycota \n(Restored vs Reference)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Basidiomycota_degraded), 
       main = "Basidiomycota \n(Restored vs Degraded)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_Basidiomycota_reference), 
       main = "Basidiomycota \n(Restored vs Reference)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
dev.off()

```

### Funnle plot composition

```{r, eval = FALSE}
png(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/funnel_plot/funnel_plot3.tiff", 
    width = 10, height = 3, units = "in", res = 300)
# Set larger margins for multi-plot layout
par(mfrow = c(1, 4), mar = c(4.5, 4.5, 4, 2), mgp = c(3, 1, 0))

funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = beta_diversity_degraded), 
       main = "Beta diversity \n(Restored vs Degraded)", 
       xlab = "Effect Size (lnRR)", ylab = "SE",
       pch = 21, bg = rgb(1, 0.5, 0, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = beta_diversity_reference), 
       main = "Beta diversity \n(Restored vs Reference)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = structure_degraded), 
       main = "Structure \n(Restored vs Degraded)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(1, 0.5, 0, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = structure_reference), 
       main = "Structure \n(Restored vs Reference)", 
       xlab = "Effect Size (lnRR)", ylab = NA,
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
dev.off()




```

```{r, eval = FALSE}
png(
    "Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/funnel_plot/funnel_plot4.tiff", 
    width = 10, height = 3, units = "in", res = 300)
# Set larger margins for multi-plot layout
par(mfrow = c(1, 4), mar = c(4.5, 4.5, 4, 2), mgp = c(3, 1, 0))
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_PLFA_degraded), 
       main = "PLFA content\n(Restored vs Degraded)", 
       xlab = "Effect Size (lnRR)", ylab = "SE",
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
funnel(rma.mv(yi, vi, random = ~ 1 | ID, data = a_PLFA_reference), 
       main = "PLFA content\n(Restored vs Reference)", 
       xlab = "Effect Size (lnRR)", ylab = "SE",
       pch = 21, bg = rgb(0, 0.805, 0.805, alpha = 0.2), col = rgb(0.5, 0.5, 0.5, alpha = 0.2), cex = 1.5,
       cex.lab = 1.2, cex.axis = 1.1, cex.main = 1.4, font.main = 1,
       las = 1, back = "white", hlines = "white")
dev.off()
```

# Overall effect of vegetation restoration

## Alpha diversity

```{r, eval = FALSE}
OTU_deg = rma.mv(yi, vi, random = ~ 1 | ID, data = a_OTU_resVsdeg)
OTU_deg
OTU_ref = rma.mv(yi, vi, random = ~ 1 | ID, data = a_OTU_resVsref)
OTU_ref
Chao_deg = rma.mv(yi, vi, random = ~ 1 | ID, data = a_Chao_resVsdeg)
Chao_deg
Chao_ref = rma.mv(yi, vi, random = ~ 1 | ID, data = a_Chao_resVsref)
Chao_ref
Shannon_deg = rma.mv(yi, vi, random = ~ 1 | ID, data = a_Shannon_resVsdeg)
Shannon_deg
Shannon_ref = rma.mv(yi, vi, random = ~ 1 | ID, data = a_Shannon_resVsref)
Shannon_ref
Simpson_deg = rma.mv(yi, vi, random = ~ 1 | ID, data = a_Simpson_resVsdeg)
Simpson_deg
Simpson_ref = rma.mv(yi, vi, random = ~ 1 | ID, data = a_Simpson_resVsref)
Simpson_ref
OTU_counts_deg <- a_OTU_resVsdeg %>%group_by(Metrics) %>%summarise(
    studies = n_distinct(ID), observations = n())
OTU_counts_ref <- a_OTU_resVsref %>%group_by(Metrics) %>% summarise(
    studies = n_distinct(ID), observations = n())
Chao_counts_deg <- a_Chao_resVsdeg %>%group_by(Metrics) %>%summarise(
    studies = n_distinct(ID), observations = n())
Chao_counts_ref <- a_Chao_resVsref %>%group_by(Metrics) %>% summarise(
    studies = n_distinct(ID), observations = n())
Shannon_counts_deg <- a_Shannon_resVsdeg %>%group_by(Metrics) %>%summarise(
    studies = n_distinct(ID), observations = n())
Shannon_counts_ref <- a_Shannon_resVsref %>%group_by(Metrics) %>% summarise(
    studies = n_distinct(ID), observations = n())
Simpson_counts_deg <- a_Simpson_resVsdeg %>%group_by(Metrics) %>%summarise(
    studies = n_distinct(ID), observations = n())
Simpson_counts_ref <- a_Simpson_resVsref %>%group_by(Metrics) %>% summarise(
    studies = n_distinct(ID), observations = n())
alpha_diversity_counts <- bind_rows(
  OTU_counts_deg %>% mutate(Comparison = "Restored vs Degraded", 
                            Metrics = "Observed richness"),
  OTU_counts_ref %>% mutate(Comparison = "Restored vs Reference", 
                            Metrics = "Observed richness"),
  Chao_counts_deg %>% mutate(Comparison = "Restored vs Degraded", 
                             Metrics = "Chao1 richness"),
  Chao_counts_ref %>% mutate(Comparison = "Restored vs Reference", 
                             Metrics = "Chao1 richness"),
   Shannon_counts_deg %>% mutate(Comparison = "Restored vs Degraded", 
                                 Metrics = "Shannon index"),
  Shannon_counts_ref %>% mutate(Comparison = "Restored vs Reference", 
                                Metrics = "Shannon index"),
  Simpson_counts_deg %>% mutate(Comparison = "Restored vs Degraded", 
                                Metrics = "Simpson index"),
  Simpson_counts_ref %>% mutate(Comparison = "Restored vs Reference", 
                                Metrics = "Simpson index")
)
OTU_mean_ci <- data.frame(
  Comparison = c("Restored vs Degraded", "Restored vs Reference"),
  Metrics    = "Observed richness",
  yi   = c(coef(OTU_deg)[1],  coef(OTU_ref)[1]),
  ci.lb      = c(OTU_deg$ci.lb[1],  OTU_ref$ci.lb[1]),
  ci.ub      = c(OTU_deg$ci.ub[1],  OTU_ref$ci.ub[1])
) %>%
  mutate(
    yi_pct = (exp(yi) - 1) * 100,
    ci.lb_pct = (exp(ci.lb) - 1) * 100,
    ci.ub_pct = (exp(ci.ub) - 1) * 100
  )
Chao_mean_ci <- data.frame(
  Comparison = c("Restored vs Degraded", "Restored vs Reference"),
  Metrics    = "Chao1 richness",
  yi   = c(coef(Chao_deg)[1],  coef(Chao_ref)[1]),
  ci.lb      = c(Chao_deg$ci.lb[1],  Chao_ref$ci.lb[1]),
  ci.ub      = c(Chao_deg$ci.ub[1],  Chao_ref$ci.ub[1])
) %>%
  mutate(
    yi_pct = (exp(yi) - 1) * 100,
    ci.lb_pct = (exp(ci.lb) - 1) * 100,
    ci.ub_pct = (exp(ci.ub) - 1) * 100
  )
Shannon_mean_ci <- data.frame(
  Comparison = c("Restored vs Degraded", "Restored vs Reference"),
  Metrics    = "Shannon index",
  yi   = c(coef(Shannon_deg)[1],  coef(Shannon_ref)[1]),
  ci.lb      = c(Shannon_deg$ci.lb[1],  Shannon_ref$ci.lb[1]),
  ci.ub      = c(Shannon_deg$ci.ub[1],  Shannon_ref$ci.ub[1])
) %>%
  mutate(
    yi_pct = (exp(yi) - 1) * 100,
    ci.lb_pct = (exp(ci.lb) - 1) * 100,
    ci.ub_pct = (exp(ci.ub) - 1) * 100
  ) 
Simpson_mean_ci <- data.frame(
  Comparison = c("Restored vs Degraded", "Restored vs Reference"),
  Metrics    = "Simpson index",
  yi   = c(coef(Simpson_deg)[1],  coef(Simpson_ref)[1]),
  ci.lb      = c(Simpson_deg$ci.lb[1],  Simpson_ref$ci.lb[1]),
  ci.ub      = c(Simpson_deg$ci.ub[1],  Simpson_ref$ci.ub[1])
) %>%
  mutate(
    yi_pct = (exp(yi) - 1) * 100,
    ci.lb_pct = (exp(ci.lb) - 1) * 100,
    ci.ub_pct = (exp(ci.ub) - 1) * 100
  ) 
alpha_diversity_mean_ci <- rbind (OTU_mean_ci,
                                  Chao_mean_ci,
                                  Shannon_mean_ci,
                                  Simpson_mean_ci)

alpha_diversity_mean_ci <- alpha_diversity_mean_ci %>%
  left_join(alpha_diversity_counts, by = c("Comparison", "Metrics")) %>%
  mutate(
    annotation = paste0("(", studies, "|", observations, ")")
  )
alpha_diversity_mean_ci <- alpha_diversity_mean_ci %>%
  mutate(Parameter = "Alpha diversity") 
```

```{r, eval = FALSE}
alpha_diversity_mean_ci

# Get common column names across ALL datasets
all_datasets <- list(
  a_OTU_resVsdeg, a_OTU_resVsref,
  a_Chao_resVsdeg, a_Chao_resVsref,
  a_Shannon_resVsdeg, a_Shannon_resVsref,
  a_Simpson_resVsdeg, a_Simpson_resVsref
)

# Find columns that are common to ALL datasets
common_cols <- Reduce(intersect, lapply(all_datasets, names))

# Combine ALL datasets with only common columns (use existing Comparison and Metrics)
combined_data <- bind_rows(
  a_OTU_resVsdeg %>% select(all_of(common_cols)),
  a_OTU_resVsref %>% select(all_of(common_cols)),
  a_Chao_resVsdeg %>% select(all_of(common_cols)),
  a_Chao_resVsref %>% select(all_of(common_cols)),
  a_Shannon_resVsdeg %>% select(all_of(common_cols)),
  a_Shannon_resVsref %>% select(all_of(common_cols)),
  a_Simpson_resVsdeg %>% select(all_of(common_cols)),
  a_Simpson_resVsref %>% select(all_of(common_cols))
)

# Convert raw yi (log scale) to percentage scale
combined_data <- combined_data %>%
  mutate(yi_pct = (exp(yi) - 1) * 100)


# Remove all specified rows
rows_to_remove <- c(984, 991, 1073, 987, 312, 314, 146, 147, 285, 284, 269, 274, 8)
combined_data_filtered <- combined_data[-rows_to_remove, ]
```

```{r, eval = FALSE}
combined_data_filtered$Metrics <- factor(combined_data_filtered$Metrics, levels = c("Simpson index",
                                                                                   "Shannon index",
                                                                                   "Chao1 richness",
                                                                                   "Observed richness"))
alpha_diversity_mean_ci$Metrics <- factor(alpha_diversity_mean_ci$Metrics, levels = c("Simpson index",
                                                                                   "Shannon index",
                                                                                   "Chao1 richness",
                                                                                   "Observed richness"))

# Plot for Restored vs Degraded
alpha_diversity_deg_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = combined_data_filtered %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics),
    position = position_jitter(height = 0.15, width = 0),
    alpha = 0.2,
    size = 3,
    shape = 21,
    fill = "orange",
      stroke = 0.1
  ) +
  geom_pointrange(
    data = alpha_diversity_mean_ci %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct),
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    fill = "black",
      stroke = 0.5,
    position = position_nudge(y = -0.005)
  ) +
  labs(x = "% Change (Alpha diversity)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
      axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )

# Plot for Restored vs Reference
alpha_diversity_ref_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = combined_data_filtered %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics),
    position = position_jitter(height = 0.15, width = 0),
   alpha = 0.2,
    size = 3,
    shape = 21,
    fill = "cyan3",
      stroke = 0.1
  ) +
  geom_pointrange(
    data = alpha_diversity_mean_ci %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct),
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    fill = "black",
      stroke = 0.5,
    position = position_nudge(y = -0.005)
  ) +
  labs(x = "% Change (Alpha diversity)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
      axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )

# Combine them
alpha_diversity_combined_plot <- grid.arrange(alpha_diversity_deg_plot, alpha_diversity_ref_plot, ncol = 2)

```

## Composition

```{r, eval = FALSE}
mod_beta_diversity_degraded <- rma.mv(yi, vi, random = ~ 1 | ID, 
                                      data = beta_diversity_degraded)
mod_beta_diversity_degraded
mod_beta_diversity_reference <- rma.mv(yi, vi, random = ~ 1 | ID, 
                                       data = beta_diversity_reference)
mod_beta_diversity_reference

mod_structure_degraded <- rma.mv(yi, vi, random = ~ 1 | ID, 
                                 data = structure_degraded)
mod_structure_degraded
mod_structure_reference <- rma.mv(yi, vi, random = ~ 1 | ID, 
                                  data = structure_reference)
mod_structure_reference
beta_diversity_mean_ci <- data.frame(
  Comparison = c("Restored vs Degraded", "Restored vs Reference"),
  Metrics    = "Beta diversity",
  yi   = c(coef(mod_beta_diversity_degraded)[1],
           coef(mod_beta_diversity_reference)[1]),
  ci.lb      = c(mod_beta_diversity_degraded$ci.lb[1],
                 mod_beta_diversity_reference$ci.lb[1]),
  ci.ub      = c(mod_beta_diversity_degraded$ci.ub[1], 
                 mod_beta_diversity_reference$ci.ub[1])
) %>%
  mutate(
    yi_pct = (exp(yi) - 1) * 100,
    ci.lb_pct = (exp(ci.lb) - 1) * 100,
    ci.ub_pct = (exp(ci.ub) - 1) * 100
  )

structure_diversity_mean_ci <- data.frame(
  Comparison = c("Restored vs Degraded", "Restored vs Reference"),
  Metrics    = "Community structure",
  yi   = c(coef(mod_structure_degraded)[1],  
           coef(mod_structure_reference)[1]),
  ci.lb      = c(mod_structure_degraded$ci.lb[1],  
                 mod_structure_reference$ci.lb[1]),
  ci.ub      = c(mod_structure_degraded$ci.ub[1],  
                 mod_structure_reference$ci.ub[1])
) %>%
  mutate(
    yi_pct = (exp(yi) - 1) * 100,
    ci.lb_pct = (exp(ci.lb) - 1) * 100,
    ci.ub_pct = (exp(ci.ub) - 1) * 100
  )
beta_diversity_Beta_compo <- rbind(beta_diversity_mean_ci, 
                                   structure_diversity_mean_ci)
counts_beta_diversity_degraded <- beta_diversity_degraded %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
counts_beta_diversity_reference <- beta_diversity_reference %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
counts_structure_degraded <- beta_diversity_degraded %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
counts_structure_reference <- beta_diversity_reference %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
all_counts <- bind_rows(
  counts_beta_diversity_degraded %>% mutate(
      Comparison = "Restored vs Degraded", 
      Metrics = "Beta diversity"),
  counts_beta_diversity_reference %>% mutate(
      Comparison = "Restored vs Reference", 
      Metrics = "Beta diversity"),
  counts_structure_degraded %>% mutate(
      Comparison = "Restored vs Degraded", 
      Metrics = "Structure"),
  counts_structure_reference %>% mutate(
      Comparison = "Restored vs Reference", 
      Metrics = "Community structure")
)
beta_diversity_Beta_compo <- beta_diversity_Beta_compo %>%
  left_join(
      all_counts, by = c("Comparison", "Metrics")) %>%
  mutate(
    annotation = paste0("(", studies, "|", observations, ")")
  )
beta_diversity_Beta_compo <- beta_diversity_Beta_compo %>%
  mutate(Parameter = "Community structure") 
```

```{r, eval = FALSE}
beta_diversity_Beta_compo

composition_raw_degraded <- bind_rows(beta_diversity_degraded,
                                      structure_degraded)
composition_raw_reference <- bind_rows(beta_diversity_reference,
                                       structure_reference)

# Get common column names between the two datasets
common_cols_composition <- intersect(names(composition_raw_degraded), names(composition_raw_reference))

# Combine with only common columns
composition_raw_combined <- bind_rows(
  composition_raw_degraded %>% select(all_of(common_cols_composition)),
  composition_raw_reference %>% select(all_of(common_cols_composition))
)

# Convert raw yi (log scale) to percentage scale
composition_raw_combined <- composition_raw_combined %>%
  mutate(yi_pct = (exp(yi) - 1) * 100)


composition_raw_combined <- composition_raw_combined %>%
  filter(yi_pct <= 400)


composition_raw_combined <- composition_raw_combined %>%
  mutate(Metrics = recode(Metrics, "Structure" = "Community structure"))

composition_raw_combined$Metrics <- factor (composition_raw_combined$Metrics, levels = c("Community structure",
                                                                                        "Beta diversity"))
beta_diversity_Beta_compo$Metrics <- factor (beta_diversity_Beta_compo$Metrics, levels = c("Community structure",
                                                                                        "Beta diversity"))


# Plot for Restored vs Degraded
beta_diversity_deg_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = composition_raw_combined %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics),
    position = position_jitter(height = 0.15, width = 0),
     alpha = 0.2,
    size = 3,
    shape = 21,
    fill = "orange",
      stroke = 0.1
  ) +
  geom_pointrange(
    data = beta_diversity_Beta_compo %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct),
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    fill = "black",
      stroke = 0.5,
    position = position_nudge(y = -0.005)
  ) +
  labs(x = "% Change (Composition)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
      axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )

# Plot for Restored vs Reference
beta_diversity_ref_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = composition_raw_combined %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics),
    position = position_jitter(height = 0.15, width = 0),
    alpha = 0.2,
    size = 3,
    shape = 21,
    fill = "cyan3",
      stroke = 0.1
  ) +
  geom_pointrange(
    data = beta_diversity_Beta_compo %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct),
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    fill = "black",
      stroke = 0.5,
    position = position_nudge(y = -0.005)
  ) +
  labs(x = "% Change (Composition)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
      axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )

# Combine them
beta_diversity_combined_plot <- grid.arrange(beta_diversity_deg_plot, beta_diversity_ref_plot, ncol = 2)
```


## Relative abundance

```{r, eval = FALSE}
mod_Ascomycota_degraded <- rma.mv(yi, vi, random = ~ 1 | ID, 
                                  data = a_Ascomycota_degraded)
mod_Ascomycota_degraded
mod_Ascomycota_reference <- rma.mv(yi, vi, random = ~ 1 | ID, 
                                   data = a_Ascomycota_reference)
mod_Ascomycota_reference
                                  
mod_Basidiomycota_degraded <- rma.mv(yi, vi, random = ~ 1 | ID, 
                                     data = a_Basidiomycota_degraded)
mod_Basidiomycota_degraded
mod_Basidiomycota_reference <- rma.mv(yi, vi, random = ~ 1 | ID, 
                                      data = a_Basidiomycota_reference)
mod_Basidiomycota_reference


Ascomycota_mean_ci <- data.frame(
  Comparison = c("Restored vs Degraded", "Restored vs Reference"),
  Metrics    = "Ascomycota",
  yi   = c(coef(mod_Ascomycota_degraded)[1],  
           coef(mod_Ascomycota_reference)[1]),
  ci.lb      = c(mod_Ascomycota_degraded$ci.lb[1],  
                 mod_Ascomycota_reference$ci.lb[1]),
  ci.ub      = c(mod_Ascomycota_degraded$ci.ub[1],  
                 mod_Ascomycota_reference$ci.ub[1])
) %>%
  mutate(
    yi_pct = (exp(yi) - 1) * 100,
    ci.lb_pct = (exp(ci.lb) - 1) * 100,
    ci.ub_pct = (exp(ci.ub) - 1) * 100
  )
Basidiomycota_mean_ci <- data.frame(
    Comparison = c("Restored vs Degraded", "Restored vs Reference"),
    Metrics    = "Basidiomycota",
  yi   = c(coef(mod_Basidiomycota_degraded)[1],  
           coef(mod_Basidiomycota_reference)[1]),
  ci.lb      = c(mod_Basidiomycota_degraded$ci.lb[1],  
                 mod_Basidiomycota_reference$ci.lb[1]),
  ci.ub      = c(mod_Basidiomycota_degraded$ci.ub[1],  
                 mod_Basidiomycota_reference$ci.ub[1])
) %>%
  mutate(
    yi_pct = (exp(yi) - 1) * 100,
    ci.lb_pct = (exp(ci.lb) - 1) * 100,
    ci.ub_pct = (exp(ci.ub) - 1) * 100
  )
Ascomycota_Basidiomycota <- rbind(Ascomycota_mean_ci, 
                                  Basidiomycota_mean_ci)
counts_Ascomycota_degraded <- a_Ascomycota_degraded %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
counts_Ascomycota_reference <- a_Ascomycota_reference %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
counts_Basidiomycota_degraded <- a_Basidiomycota_degraded %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
counts_Basidiomycota_reference <- a_Basidiomycota_reference %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
all_counts <- bind_rows(
  counts_Ascomycota_degraded %>% mutate(
      Comparison = "Restored vs Degraded", 
      Metrics = "Ascomycota"),
  counts_Ascomycota_reference %>% mutate(
      Comparison = "Restored vs Reference", 
      Metrics = "Ascomycota"),
  counts_Basidiomycota_degraded %>% mutate(
      Comparison = "Restored vs Degraded", 
      Metrics = "Basidiomycota"),
  counts_Basidiomycota_reference %>% mutate(
      Comparison = "Restored vs Reference", 
      Metrics = "Basidiomycota")
)
Ascomycota_Basidiomycota_combined <- Ascomycota_Basidiomycota %>%
  left_join(all_counts, by = c("Comparison", "Metrics")) %>%
  mutate(
    annotation = paste0("(", studies, "|", observations, ")")
  )
Ascomycota_Basidiomycota_combined <- Ascomycota_Basidiomycota_combined %>%
  mutate(Parameter = "Relative abundance") 
```

```{r, eval = FALSE}
Ascomycota_Basidiomycota_combined

# Get common column names between the two datasets
common_cols_abundance <- intersect(names(Ascomycota_Basidiomycota_deg_raw), names(Ascomycota_Basidiomycota_ref_raw))

# Combine with only common columns
abundance_raw_combined <- bind_rows(
  Ascomycota_Basidiomycota_deg_raw %>% select(all_of(common_cols_abundance)),
  Ascomycota_Basidiomycota_ref_raw %>% select(all_of(common_cols_abundance))
)

# Convert raw yi (log scale) to percentage scale
abundance_raw_combined <- abundance_raw_combined %>%
  mutate(yi_pct = (exp(yi) - 1) * 100)

abundance_raw_combined <- abundance_raw_combined %>%
  filter(yi_pct <= 500)


abundance_raw_combined$Metrics <- factor (abundance_raw_combined$Metrics, levels = c("Basidiomycota",
                                                                                    "Ascomycota"))
Ascomycota_Basidiomycota_combined$Metrics <- factor (Ascomycota_Basidiomycota_combined$Metrics, levels = c("Basidiomycota",
                                                                                    "Ascomycota"))



# Plot for Restored vs Degraded
abundance_deg_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = abundance_raw_combined %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics),
    position = position_jitter(height = 0.15, width = 0),
     alpha = 0.2,
    size = 3,
    shape = 21,
    fill = "orange",
      stroke = 0.1
  ) +
  geom_pointrange(
    data = Ascomycota_Basidiomycota_combined %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct),
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    fill = "black",
      stroke = 0.5,
    position = position_nudge(y = -0.005)
  ) +
  labs(x = "% Change (Relative abundance)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
      axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )

# Plot for Restored vs Reference
abundance_ref_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = abundance_raw_combined %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics),
    position = position_jitter(height = 0.15, width = 0),
    alpha = 0.2,
    size = 3,
    shape = 21,
    fill = "cyan3",
      stroke = 0.1
  ) +
  geom_pointrange(
    data = Ascomycota_Basidiomycota_combined %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct),
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    fill = "black",
      stroke = 0.5,
    position = position_nudge(y = -0.005)
  ) +
  labs(x = "% Change (Relative abundance)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
      axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )

# Combine them
abundance_combined_plot <- grid.arrange(abundance_deg_plot, abundance_ref_plot, ncol = 2)
```

## Biomass

```{r, eval = FALSE}
mod_PLFA_degraded <- rma.mv(yi, vi, random = ~ 1 | ID, 
                            data = a_PLFA_degraded)
mod_PLFA_degraded
mod_PLFA_reference <- rma.mv(yi, vi, random = ~ 1 | ID, 
                             data = a_PLFA_reference)
mod_PLFA_reference
PLFA_mean_ci <- data.frame(
  Comparison = c("Restored vs Degraded", "Restored vs Reference"),
  Metrics    = "PLFA content",
  yi   = c(coef(mod_PLFA_degraded)[1],  coef(mod_PLFA_reference)[1]),
  ci.lb      = c(mod_PLFA_degraded$ci.lb[1],  mod_PLFA_reference$ci.lb[1]),
  ci.ub      = c(mod_PLFA_degraded$ci.ub[1],  mod_PLFA_reference$ci.ub[1])
) %>%
  mutate(
    yi_pct = (exp(yi) - 1) * 100,
    ci.lb_pct = (exp(ci.lb) - 1) * 100,
    ci.ub_pct = (exp(ci.ub) - 1) * 100
  )
counts_PLFA_degraded <- a_PLFA_degraded %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
counts_PLFA_reference <- a_PLFA_reference %>%
  group_by(Metrics) %>%
  summarise(
    studies = n_distinct(ID),
    observations = n()
  )
all_counts <- bind_rows(
  counts_PLFA_degraded %>% mutate(Comparison = "Restored vs Degraded", 
                                  Metrics = "PLFA content"),
  counts_PLFA_reference %>% mutate(Comparison = "Restored vs Reference", 
                                   Metrics = "PLFA content")
)
PLFA_mean_ci_combined <- PLFA_mean_ci %>%
  left_join(all_counts, by = c("Comparison", "Metrics")) %>%
  mutate(
    annotation = paste0("(", studies, "|", observations, ")")
  )
PLFA_mean_ci_combined <- PLFA_mean_ci_combined %>%
  mutate(Parameter = "Biomass") 

```

```{r, eval = FALSE}
PLFA_mean_ci_combined

# Get common column names between the two datasets
common_cols_plfa <- intersect(names(a_PLFA_degraded), names(a_PLFA_reference))

# Combine with only common columns
plfa_raw_combined <- bind_rows(
  a_PLFA_degraded %>% select(all_of(common_cols_plfa)),
  a_PLFA_reference %>% select(all_of(common_cols_plfa))
)

# Convert raw yi (log scale) to percentage scale
plfa_raw_combined <- plfa_raw_combined %>%
  mutate(yi_pct = (exp(yi) - 1) * 100)

plfa_raw_combined <- plfa_raw_combined %>%
  filter(yi_pct <= 500)

# Plot for Restored vs Degraded
plfa_deg_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = plfa_raw_combined %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics),
    position = position_jitter(height = 0.15, width = 0),
     alpha = 0.2,
    size = 3,
    shape = 21,
    fill = "orange",
      stroke = 0.1
  ) +
  geom_pointrange(
    data = PLFA_mean_ci_combined %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct),
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    fill = "black",
      stroke = 0.5,
    position = position_nudge(y = -0.005)
  ) +
  labs(x = "% Change (Biomass)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
      axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )

# Plot for Restored vs Reference
plfa_ref_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = plfa_raw_combined %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics),
    position = position_jitter(height = 0.15, width = 0),
    alpha = 0.2,
    size = 3,
    shape = 21,
    fill = "cyan3",
      stroke = 0.1
  ) +
  geom_pointrange(
    data = PLFA_mean_ci_combined %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct),
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    fill = "black",
      stroke = 0.5,
    position = position_nudge(y = -0.005)
  ) +
  labs(x = "% Change (Biomass)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
      axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )
plfa_ref_plot
# Arrange them side by side
plfa_combined_plot <- grid.arrange(plfa_deg_plot, plfa_ref_plot, ncol = 2)


```

## Figure 2
```{r, eval = FALSE}
combined_plot_deg1 <- grid.arrange(
  alpha_diversity_deg_plot, 
  plfa_deg_plot,
    nrow = 2, 
  heights = c(1, 0.4)
)
combined_plot_deg1


combined_plot_deg2 <- grid.arrange(
    abundance_deg_plot,
  beta_diversity_deg_plot, 
    nrow = 2,
  heights = c(1, 1)  # Equal row heights
)
combined_plot_deg2


combined_plot_deg3 <- grid.arrange(
  combined_plot_deg1,
  combined_plot_deg2,
  ncol   = 2,
  widths = c(1, 1),
  top    = textGrob("Restored vs Degraded",
                    gp = gpar(fontsize = 12, fontface = "bold"))
)
combined_plot_deg3




combined_plot_ref4 <- grid.arrange(
  alpha_diversity_ref_plot, 
  plfa_ref_plot,
    nrow = 2, 
  heights = c(1, 0.4)
)
combined_plot_ref4


combined_plot_ref5 <- grid.arrange(
    abundance_ref_plot,
  beta_diversity_ref_plot,
    nrow = 2,
  heights = c(1, 1)  # Equal row heights
)
combined_plot_ref5


combined_plot_ref6 <- grid.arrange(
  combined_plot_ref4,
  combined_plot_ref5,
  ncol   = 2,
  widths = c(1, 1),
  top    = textGrob("Restored vs Reference",
                    gp = gpar(fontsize = 12, fontface = "bold"))
)

combined_plot_ref6


```

```{r, eval = FALSE}

ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/overall/figure_2.1.jpg",
       combined_plot_deg3, dpi = 600, height = 5, width = 5)



ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/overall/figure_2.2.jpg",
       combined_plot_ref6, dpi = 600, height = 5, width = 5)
```


# Effect of restoration strategy

```{r, eval = FALSE}
get_predictions <- function(model, data, comparison_type, metric_type) {
   pred_grid <- data.frame(
    Restoration_strategy = levels(data$Restoration_strategy)
  )
   predictions <- predict(model, 
                        newmods = model.matrix(~ Restoration_strategy, 
                                               data = pred_grid)[,-1, 
                                                                 drop = FALSE])
    study_counts <- data %>%
    group_by(Restoration_strategy) %>%
    summarize(
      n_studies = n_distinct(ID),
      n_observations = n()
    )
    results <- data.frame(
    Restoration_strategy = pred_grid$Restoration_strategy,
    pred = predictions$pred,
    se = predictions$se,
    ci.lb = predictions$ci.lb,
    ci.ub = predictions$ci.ub,
    Comparison = comparison_type,
    Metrics = metric_type
  )
  results <- results %>%
    left_join(study_counts, by = "Restoration_strategy") %>%
    mutate(
      annotation = paste0("(", n_studies, "|", n_observations, ")")
    )
    return(results)
}
```

## Alpha diversity

```{r, eval = FALSE}
OTU_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                        random = ~ 1 | ID, data = a_OTU_resVsdeg)
OTU_deg_model
OTU_ref_model <-rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                       random = ~ 1 | ID, data = a_OTU_resVsref) 
OTU_ref_model
Chao_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                         random = ~ 1 | ID, data = a_Chao_resVsdeg)
Chao_deg_model
Chao_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                         random = ~ 1 | ID, data = a_Chao_resVsref)
Chao_ref_model
Shannon_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                            random = ~ 1 | ID, data = a_Shannon_resVsdeg)
Shannon_deg_model
Shannon_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                            random = ~ 1 | ID, data = a_Shannon_resVsref)
Shannon_ref_model
Simpson_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                            random = ~ 1 | ID, data = a_Simpson_resVsdeg)
Simpson_deg_model
Simpson_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                            random = ~ 1 | ID, data = a_Simpson_resVsref)
Simpson_ref_model
OTU_deg_predictions <- get_predictions(OTU_deg_model, 
                                       a_OTU_resVsdeg, 
                                       "Restored vs Degraded", 
                                       "Observed richness")
OTU_ref_predictions <- get_predictions(OTU_ref_model, 
                                       a_OTU_resVsref, 
                                       "Restored vs Reference", 
                                       "Observed richness")
Chao_deg_predictions <- get_predictions(Chao_deg_model, 
                                        a_Chao_resVsdeg, 
                                        "Restored vs Degraded", 
                                        "Chao1 richness")
Chao_ref_predictions <- get_predictions(Chao_ref_model, 
                                        a_Chao_resVsref, 
                                        "Restored vs Reference", 
                                        "Chao1 richness")
Shannon_deg_predictions <- get_predictions(Shannon_deg_model, 
                                           a_Shannon_resVsdeg, 
                                           "Restored vs Degraded", 
                                           "Shannon index")
Shannon_ref_predictions <- get_predictions(Shannon_ref_model, 
                                           a_Shannon_resVsref, 
                                           "Restored vs Reference", 
                                           "Shannon index")
Simpson_deg_predictions <- get_predictions(Simpson_deg_model,
                                           a_Simpson_resVsdeg, 
                                           "Restored vs Degraded", 
                                           "Simpson index")
Simpson_ref_predictions <- get_predictions(Simpson_ref_model, 
                                           a_Simpson_resVsref, 
                                           "Restored vs Reference", 
                                           "Simpson index")
all_predictions_alpha_diversity <- bind_rows(
  OTU_deg_predictions,
  OTU_ref_predictions,
  Chao_deg_predictions,
  Chao_ref_predictions,
  Shannon_deg_predictions,
  Shannon_ref_predictions,
  Simpson_deg_predictions,
  Simpson_ref_predictions)
all_predictions_alpha_diversity <- all_predictions_alpha_diversity %>%
  mutate(
    pred_pct = pred * 100,  
    ci.lb_pct = ci.lb * 100,
    ci.ub_pct = ci.ub * 100
  )
all_predictions_alpha_diversity <- all_predictions_alpha_diversity %>%
  mutate(Parameter = "Alpha diversity")
```

```{r, eval = FALSE}
all_predictions_alpha_diversity



all_predictions_alpha_diversity$Metrics <- factor (all_predictions_alpha_diversity$Metrics, levels = c("Simpson index", "Shannon index", "Chao1 richness", "Observed richness"))
combined_data_filtered$Metrics <- factor (combined_data_filtered$Metrics, levels = c("Simpson index", "Shannon index", "Chao1 richness", "Observed richness"))

combined_data_filtered

alpha_diversity_restoration_deg_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = combined_data_filtered %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics, fill = Restoration_strategy),
    position = position_jitterdodge(
      jitter.width = 0.1,    # Horizontal jitter
      jitter.height = 0.1,   # Vertical jitter
      dodge.width = 0.8      # Dodge width
    ),
    alpha = 0.2,
    size = 3,
    shape = 21,
    stroke = 0.1,
      color ="black"
  ) +
  geom_pointrange(
    data = all_predictions_alpha_diversity %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = pred_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct, group = Restoration_strategy),
    color = "black",
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    stroke = 0.5,
    fill = "black",
    position = position_dodge(width = 0.8)
  ) +
  scale_fill_manual(values = c("Active" = "#F8766D", "Passive" = "#7CAE00")) +
  coord_cartesian(xlim = c(-80, 120)) +  # Adjust these values as needed
  labs(x = "% Change (Alpha diversity)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )
alpha_diversity_restoration_deg_plot





alpha_diversity_restoration_ref_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = combined_data_filtered %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics, fill = Restoration_strategy),
    position = position_jitterdodge(
      jitter.width = 0.1,    # Horizontal jitter
      jitter.height = 0.1,   # Vertical jitter
      dodge.width = 0.8      # Dodge width
    ),
    alpha = 0.2,
    size = 3,
    shape = 21,
    stroke = 0.1,
      color ="black"
  ) +
  geom_pointrange(
    data = all_predictions_alpha_diversity %>% filter(Comparison == "Restored vs Reference"),
    aes(x = pred_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct, group = Restoration_strategy),
    color = "black",
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    stroke = 0.5,
    fill = "black",
    position = position_dodge(width = 0.8)
  ) +
  scale_fill_manual(values = c("Active" = "#F8766D", "Passive" = "#7CAE00")) +
  labs(x = "% Change (Alpha diversity)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )
alpha_diversity_restoration_ref_plot

```

## Composition

```{r, eval = FALSE}
beta_diversity_degraded
beta_diversity_reference
structure_degraded
structure_reference
beta_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                         random = ~ 1 | ID, 
                         data = beta_diversity_degraded)
beta_deg_model
beta_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy , 
                         random = ~ 1 | ID, 
                         data = beta_diversity_reference)
beta_ref_model
structure_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy , 
                              random = ~ 1 | ID, 
                              data = structure_degraded)
structure_deg_model
structure_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy , 
                              random = ~ 1 | ID, 
                              data = structure_reference)
structure_ref_model
beta_deg_predictions <- get_predictions(beta_deg_model, 
                                        beta_diversity_degraded, 
                                        "Restored vs Degraded", 
                                        "Beta diversity")
beta_ref_predictions <- get_predictions(beta_ref_model, 
                                        beta_diversity_reference,
                                        "Restored vs Reference", 
                                        "Beta diversity")
comp_deg_predictions <- get_predictions(structure_deg_model, 
                                        structure_degraded, 
                                        "Restored vs Degraded", 
                                        "Community structure")
comp_ref_predictions <- get_predictions(structure_ref_model, 
                                        structure_reference, 
                                        "Restored vs Reference", 
                                        "Community structure")
all_predictions_composition <- bind_rows(
  beta_deg_predictions,
  beta_ref_predictions,
  comp_deg_predictions,
  comp_ref_predictions
)
all_predictions_composition <- all_predictions_composition %>%
  mutate(
      pred_pct = pred * 100, 
      ci.lb_pct = ci.lb * 100, 
      ci.ub_pct = ci.ub * 100)
all_predictions_composition <- all_predictions_composition %>% mutate(
    Parameter = "Composition")
```

```{r, eval = FALSE}
all_predictions_composition

composition_raw_combined
composition_raw_combined <- composition_raw_combined %>%
  mutate(Metrics = recode(Metrics, "Structure" = "Community structure"))


all_predictions_composition
all_predictions_composition$Metrics <- factor (all_predictions_composition$Metrics, levels = c("Community structure", "Beta diversity"))
composition_raw_combined$Metrics <- factor (composition_raw_combined$Metrics, levels = c("Community structure", "Beta diversity"))




composition_restoration_deg_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = composition_raw_combined %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics, fill = Restoration_strategy),
    position = position_jitterdodge(
      jitter.width = 0.1,    # Horizontal jitter
      jitter.height = 0.1,   # Vertical jitter
      dodge.width = 0.8      # Dodge width
    ),
    alpha = 0.2,
    size = 3,
    shape = 21,
    stroke = 0.1,
      color ="black"
  ) +
  geom_pointrange(
    data = all_predictions_composition %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = pred_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct, group = Restoration_strategy),
    color = "black",
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    stroke = 0.5,
    fill = "black",
    position = position_dodge(width = 0.8)
  ) +
  scale_fill_manual(values = c("Active" = "#F8766D", "Passive" = "#7CAE00")) +
  coord_cartesian(xlim = c(-100, 380)) +  # Adjust these values as needed
  labs(x = "% Change (Composition)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )
composition_restoration_deg_plot


composition_restoration_ref_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = composition_raw_combined %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics, fill = Restoration_strategy),
    position = position_jitterdodge(
      jitter.width = 0.1,    # Horizontal jitter
      jitter.height = 0.1,   # Vertical jitter
      dodge.width = 0.8      # Dodge width
    ),
    alpha = 0.2,
    size = 3,
    shape = 21,
    stroke = 0.1,
      color ="black"
  ) +
  geom_pointrange(
    data = all_predictions_composition %>% filter(Comparison == "Restored vs Reference"),
    aes(x = pred_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct, group = Restoration_strategy),
    color = "black",
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    stroke = 0.5,
    fill = "black",
    position = position_dodge(width = 0.8)
  ) +
  scale_fill_manual(values = c("Active" = "#F8766D", "Passive" = "#7CAE00")) +
  coord_cartesian(xlim = c(-100, 305)) +  # Adjust these values as needed
  labs(x = "% Change (Composition)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )
composition_restoration_ref_plot
```

## Relative abundance

```{r, eval = FALSE}
Ascomycota_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                               random = ~ 1 | ID, 
                               data = a_Ascomycota_degraded)
Ascomycota_deg_model
Ascomycota_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy , 
                               random = ~ 1 | ID, 
                               data = a_Ascomycota_reference)
Ascomycota_ref_model
Basidiomycota_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy , 
                                  random = ~ 1 | ID, 
                                  data = a_Basidiomycota_degraded)
Basidiomycota_deg_model
Basidiomycota_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy , 
                                  random = ~ 1 | ID, 
                                  data = a_Basidiomycota_reference)
Basidiomycota_ref_model
Ascomycota_deg_predictions <- get_predictions(Ascomycota_deg_model, 
                                              a_Ascomycota_degraded, 
                                              "Restored vs Degraded", 
                                              "Ascomycota")
Ascomycota_ref_predictions <- get_predictions(Ascomycota_ref_model, 
                                              a_Ascomycota_reference, 
                                              "Restored vs Reference", 
                                              "Ascomycota")
Basidiomycota_deg_predictions <- get_predictions(Basidiomycota_deg_model, 
                                                 a_Basidiomycota_degraded, 
                                                 "Restored vs Degraded", 
                                                 "Basidiomycota")
Basidiomycota_ref_predictions <- get_predictions(Basidiomycota_ref_model, 
                                                 a_Basidiomycota_reference, 
                                                 "Restored vs Reference", 
                                                 "Basidiomycota")
all_predictions_abundance <- bind_rows(
  Ascomycota_deg_predictions,
  Ascomycota_ref_predictions,
  Basidiomycota_deg_predictions,
  Basidiomycota_ref_predictions
)
all_predictions_abundance <- all_predictions_abundance %>%
  mutate(
    pred_pct = pred * 100,  
    ci.lb_pct = ci.lb * 100,
    ci.ub_pct = ci.ub * 100
  )
all_predictions_abundance <- all_predictions_abundance %>%
  mutate(Parameter = "Relative abundance")
```

```{r, eval = FALSE}
all_predictions_abundance
abundance_raw_combined


all_predictions_abundance
all_predictions_abundance$Metrics <- factor (all_predictions_abundance$Metrics, levels = c("Basidiomycota", "Ascomycota"))
abundance_raw_combined$Metrics <- factor (abundance_raw_combined$Metrics, levels = c("Basidiomycota", "Ascomycota"))



abundance_restoration_deg_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = abundance_raw_combined %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics, fill = Restoration_strategy),
    position = position_jitterdodge(
      jitter.width = 0.1,    # Horizontal jitter
      jitter.height = 0.1,   # Vertical jitter
      dodge.width = 0.8      # Dodge width
    ),
    alpha = 0.2,
    size = 3,
    shape = 21,
    stroke = 0.1,
      color ="black"
  ) +
  geom_pointrange(
    data = all_predictions_abundance %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = pred_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct, group = Restoration_strategy),
    color = "black",
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    stroke = 0.5,
    fill = "black",
    position = position_dodge(width = 0.8)
  ) +
  scale_fill_manual(values = c("Active" = "#F8766D", "Passive" = "#7CAE00")) +
coord_cartesian(xlim = c(-100, 400)) + 
  labs(x = "% Change (Relative abundance)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )
abundance_restoration_deg_plot


abundance_restoration_ref_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = abundance_raw_combined %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics, fill = Restoration_strategy),
    position = position_jitterdodge(
      jitter.width = 0.1,    # Horizontal jitter
      jitter.height = 0.1,   # Vertical jitter
      dodge.width = 0.8      # Dodge width
    ),
    alpha = 0.2,
    size = 3,
    shape = 21,
    stroke = 0.1,
      color ="black"
  ) +
  geom_pointrange(
    data = all_predictions_abundance %>% filter(Comparison == "Restored vs Reference"),
    aes(x = pred_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct, group = Restoration_strategy),
    color = "black",
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    stroke = 0.5,
    fill = "black",
    position = position_dodge(width = 0.8)
  ) +
  scale_fill_manual(values = c("Active" = "#F8766D", "Passive" = "#7CAE00")) +
coord_cartesian(xlim = c(-100, 300)) + 
  labs(x = "% Change (Relative abundance)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )
abundance_restoration_ref_plot
```

## Biomass

```{r, eval = FALSE}
plfa_deg_restoration_model <- rma.mv(yi, vi, mods = ~ Restoration_strategy, 
                                     random = ~ 1 | ID, 
                                     data = a_PLFA_degraded)
plfa_deg_restoration_model
16
plfa_deg_predictions <- get_predictions(plfa_deg_restoration_model, 
                                        a_PLFA_degraded, 
                                        "Restored vs Degraded", 
                                        "PLFA content")
plfa_ref_predictions <- get_predictions(plfa_ref_restoration_model, 
                                        a_PLFA_reference, 
                                        "Restored vs Reference", 
                                        "PLFA content")
all_predictions_plfa <- bind_rows(
  plfa_deg_predictions,
  plfa_ref_predictions
)
all_predictions_plfa <- all_predictions_plfa %>%
  mutate(
    pred_pct = pred * 100,  
    ci.lb_pct = ci.lb * 100,
    ci.ub_pct = ci.ub * 100
  )
all_predictions_plfa <- all_predictions_plfa %>%
  mutate(Parameter = "Biomass")
```

```{r, eval = FALSE}
all_predictions_plfa
plfa_raw_combined


plfa_restoration_deg_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = plfa_raw_combined %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics, fill = Restoration_strategy),
    position = position_jitterdodge(
      jitter.width = 0.1,    # Horizontal jitter
      jitter.height = 0.1,   # Vertical jitter
      dodge.width = 0.8      # Dodge width
    ),
    alpha = 0.5,
    size = 3,
    shape = 21,
    stroke = 0.1,
      color ="black"
  ) +
  geom_pointrange(
    data = all_predictions_plfa %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = pred_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct, group = Restoration_strategy),
    color = "black",
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    stroke = 0.5,
    fill = "black",
    position = position_dodge(width = 0.8)
  ) +
  scale_fill_manual(values = c("Active" = "#F8766D", "Passive" = "#7CAE00")) +
coord_cartesian(xlim = c(-100, 300)) + 
  labs(x = "% Change (Biomass)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )
plfa_restoration_deg_plot


plfa_restoration_ref_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = plfa_raw_combined %>% filter(Comparison == "Restored vs Reference"),
    aes(x = yi_pct, y = Metrics, fill = Restoration_strategy),
    position = position_jitterdodge(
      jitter.width = 0.1,    # Horizontal jitter
      jitter.height = 0.1,   # Vertical jitter
      dodge.width = 0.8      # Dodge width
    ),
    alpha = 0.5,
    size = 3,
    shape = 21,
    stroke = 0.1,
      color ="black"
  ) +
  geom_pointrange(
    data = all_predictions_plfa %>% filter(Comparison == "Restored vs Reference"),
    aes(x = pred_pct, y = Metrics, xmin = ci.lb_pct, xmax = ci.ub_pct, group = Restoration_strategy),
    color = "black",
    size = 0.5,
    shape = 1,
    linewidth = 0.5,
    stroke = 0.5,
    fill = "black",
    position = position_dodge(width = 0.8)
  ) +
  scale_fill_manual(values = c("Active" = "#F8766D", "Passive" = "#7CAE00")) +
  labs(x = "% Change (Biomass)", y = NULL) +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "plain", size = 14),
    axis.title = element_text(face = "plain", size = 12),
    axis.text = element_text(size = 10, color = "black"),
    panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA)
  )
plfa_restoration_ref_plot
```

## Figure 3

```{r, eval = FALSE}
plot_with_legend <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(
    data = combined_data_filtered %>% filter(Comparison == "Restored vs Degraded"),
    aes(x = yi_pct, y = Metrics, fill = Restoration_strategy),
    position = position_jitterdodge(
      jitter.width = 0.2,
      jitter.height = 0.1,
      dodge.width = 0.8
    ),
    alpha = 0.5,
    size = 3,
    shape = 21,
    stroke = 0.1,
    color = "black"
  ) +
theme_bw()+
  scale_fill_manual(values = c("Active" = "#F8766D", "Passive" = "#7CAE00"),
                   name = "Restoration strategy",
                   labels = c("Active" = "Active restoration", "Passive" = "Natural regeneration") ) +
  theme(legend.position = "bottom",
        panel.grid.major = element_line(color = "transparent"),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(color = "black", fill = NA),
       legend.text = element_text(size = 12))
plot_with_legend


# Extract the legend
get_legend <- function(plot) {
  grob_table <- ggplot_gtable(ggplot_build(plot))
  legend_index <- which(sapply(grob_table$grobs, function(x) x$name) == "guide-box")
  legend <- grob_table$grobs[[legend_index]]
  return(legend)
}

legend <- get_legend(plot_with_legend)
```

```{r, eval = FALSE}

combined_plot_deg11 <- grid.arrange(
  alpha_diversity_restoration_deg_plot, 
  plfa_restoration_ref_plot,
    nrow = 2, 
  heights = c(1, 0.4)
)
combined_plot_deg11


combined_plot_deg12 <- grid.arrange(abundance_restoration_deg_plot,
  composition_restoration_deg_plot,
    nrow = 2,
  heights = c(1, 1)  # Equal row heights
)
combined_plot_deg12



# Final plot with legend
combined_plot_deg13 <- grid.arrange(
  combined_plot_deg11,
  combined_plot_deg12,
  legend,
  ncol = 2,
  nrow = 2,
  layout_matrix = rbind(c(1, 2), c(3, 3)),  # Legend spans both columns in second row
  heights = c(10, 1),  # Adjust heights to give more space to plots, less to legend
  top = textGrob("Restored vs Degraded",
                gp = gpar(fontsize = 12, fontface = "bold"))
)

combined_plot_deg13




combined_plot_ref14 <- grid.arrange(
  alpha_diversity_restoration_ref_plot, 
  plfa_restoration_ref_plot,
    nrow = 2, 
  heights = c(1, 0.4)
)
combined_plot_ref14


combined_plot_ref15 <- grid.arrange(abundance_restoration_ref_plot,
  composition_restoration_ref_plot,
    nrow = 2,
  heights = c(1, 1)  # Equal row heights
)
combined_plot_ref15


combined_plot_ref16 <- grid.arrange(
  combined_plot_ref14,
  combined_plot_ref15,
  legend,
  ncol = 2,
  nrow = 2,
  layout_matrix = rbind(c(1, 2), c(3, 3)),  # Legend spans both columns in second row
  heights = c(10, 1),  # Adjust heights to give more space to plots, less to legend
  top = textGrob("Restored vs Reference",
                gp = gpar(fontsize = 12, fontface = "bold"))
)

combined_plot_ref16

```

```{r, eval = FALSE}
ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/restoration_strategy/figure_3.1.jpg",
       combined_plot_deg13, dpi = 600, height = 8, width = 5)



ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/restoration_strategy/figure_3.2.jpg",
       combined_plot_ref16, dpi = 600, height = 8, width = 5)
```

# Effect of restoration time

```{r, eval = FALSE}
get_time_predictions <- function(model, dataset) {
  time_seq <- seq(min(dataset$Restoration_time), 
                  max(dataset$Restoration_time), length.out = 50)
  pred <- predict(model, newmods = time_seq)
  
  data.frame(
    Restoration_time = time_seq,
    pred = pred$pred,
    ci.lb = pred$ci.lb,
    ci.ub = pred$ci.ub
  )
}
```

## Alpha diversity

```{r, eval = FALSE}
OTU_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_time, 
                        random = ~ 1 | ID, data = a_OTU_resVsdeg)
OTU_deg_model
OTU_ref_model <-rma.mv(yi, vi, mods = ~ Restoration_time, 
                       random = ~ 1 | ID, data = a_OTU_resVsref) 
OTU_ref_model
Chao_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_time, 
                         random = ~ 1 | ID, data = a_Chao_resVsdeg)
Chao_deg_model
Chao_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_time, 
                         random = ~ 1 | ID, data = a_Chao_resVsref)
Chao_ref_model
Shannon_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_time, 
                            random = ~ 1 | ID, data = a_Shannon_resVsdeg)
Shannon_deg_model
Shannon_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_time, 
                            random = ~ 1 | ID, data = a_Shannon_resVsref)
Shannon_ref_model
Simpson_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_time, 
                            random = ~ 1 | ID, data = a_Simpson_resVsdeg)
Simpson_deg_model
Simpson_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_time, 
                            random = ~ 1 | ID, data = a_Simpson_resVsref)
Simpson_ref_model
OTU_deg_predictions_time <- get_time_predictions(OTU_deg_model, 
                                                 a_OTU_resVsdeg)
OTU_ref_predictions_time <- get_time_predictions(OTU_ref_model, 
                                                 a_OTU_resVsref)
Chao_deg_predictions_time <- get_time_predictions(Chao_deg_model, 
                                                  a_Chao_resVsdeg)
Chao_ref_predictions_time <- get_time_predictions(Chao_ref_model, 
                                                  a_Chao_resVsref)
Shannon_deg_predictions_time <- get_time_predictions(Shannon_deg_model, 
                                                     a_Shannon_resVsdeg)
Shannon_ref_predictions_time <- get_time_predictions(Shannon_ref_model, 
                                                     a_Shannon_resVsref)
Simpson_deg_predictions_time <- get_time_predictions(Simpson_deg_model, 
                                                     a_Simpson_resVsdeg)
Simpson_ref_predictions_time <- get_time_predictions(Simpson_ref_model, 
                                                     a_Simpson_resVsref)
OTU_deg_predictions_time$Comparison <- "Restored vs Degraded"
OTU_deg_predictions_time$Metrics <- "Observed richness"
OTU_ref_predictions_time$Comparison <- "Restored vs Reference"
OTU_ref_predictions_time$Metrics <- "Observed richness"
Chao_deg_predictions_time$Comparison <- "Restored vs Degraded"
Chao_deg_predictions_time$Metrics <- "Chao1 richness"
Chao_ref_predictions_time$Comparison <- "Restored vs Reference"
Chao_ref_predictions_time$Metrics <- "Chao1 richness"
Shannon_deg_predictions_time$Comparison <- "Restored vs Degraded"
Shannon_deg_predictions_time$Metrics <- "Shannon index"
Shannon_ref_predictions_time$Comparison <- "Restored vs Reference"
Shannon_ref_predictions_time$Metrics <- "Shannon index"
Simpson_deg_predictions_time$Comparison <- "Restored vs Degraded"
Simpson_deg_predictions_time$Metrics <- "Simpson index"
Simpson_ref_predictions_time$Comparison <- "Restored vs Reference"
Simpson_ref_predictions_time$Metrics <- "Simpson index"
alpha_time_predictions_deg <- rbind(
  OTU_deg_predictions_time, 
    Chao_deg_predictions_time, 
    Shannon_deg_predictions_time, 
    Simpson_deg_predictions_time
)%>% mutate(Parameter = "Alpha diversity")
alpha_time_predictions_ref <- rbind(
  OTU_ref_predictions_time, 
    Chao_ref_predictions_time, 
    Shannon_ref_predictions_time, 
    Simpson_ref_predictions_time
)%>% mutate(Parameter = "Alpha diversity")
alpha_time_predictions_deg <- alpha_time_predictions_deg[-c(394,408, 717), ]

alpha_diversity_deg_raw_time <- alpha_diversity_deg_raw %>%
  mutate(Parameter = "Alpha diversity") %>%
  select(yi, vi, Restoration_time, Metrics, Comparison, Parameter)

alpha_diversity_ref_raw_time <- alpha_diversity_ref_raw %>%
  mutate(Parameter = "Alpha diversity") %>%
  select(yi, vi, Restoration_time, Metrics, Comparison, Parameter)
```

```{r, eval = FALSE}
alpha_time_ppt_1 <- ggplot(alpha_time_predictions_deg, aes(x = Restoration_time, 
                                           y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = alpha_diversity_deg_raw_time, aes(y = yi), 
             alpha = 0.3, size = 1.5, 
             shape = 21, fill = "orange", 
             fill = "white") +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.3, 
              fill = "grey") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(
    x = "Restoration time (Yrs)",
    y = "lnRR (Alpha diversity)"
  ) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()
  ) +
  facet_wrap(~Metrics, scales = "free", ncol = 4)

alpha_time_ppt_1

alpha_time_ppt_2 <- ggplot(alpha_time_predictions_ref, aes(x = Restoration_time, 
                                           y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = alpha_diversity_ref_raw_time, aes(y = yi), 
             alpha = 0.3, size = 1.5, 
             shape = 1, color = "grey30", 
             fill = "white") +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.3, 
              fill = "darkgreen") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(title = "Alpha diversity",
    x = "Restoration time (Yrs)",
    y = "lnRR"
  ) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()
  ) +
  facet_wrap(~Metrics, scales = "free", ncol = 4)

alpha_time_ppt_2

```

## Composition

```{r, eval = FALSE}
beta_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_time, 
                         random = ~ 1 | ID, 
                         data = beta_diversity_degraded)
beta_deg_model
beta_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_time , 
                         random = ~ 1 | ID, 
                         data = beta_diversity_reference)
beta_ref_model
structure_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_time , 
                              random = ~ 1 | ID, 
                              data = structure_degraded)
structure_deg_model
structure_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_time , 
                              random = ~ 1 | ID, 
                              data = structure_reference)
structure_ref_model
beta_deg_pred <- get_time_predictions(beta_deg_model, 
                                      beta_diversity_degraded)
structure_deg_pred <- get_time_predictions(structure_deg_model, 
                                           structure_degraded)
beta_deg_pred$Metrics <- "Beta diversity"
beta_deg_pred$Comparison <- "Restored vs Degraded"
structure_deg_pred$Metrics <- "Community structure"
structure_deg_pred$Comparison <- "Restored vs Degraded"
composition_time_predictions_deg <- rbind(
  beta_deg_pred, structure_deg_pred
)%>% mutate(Parameter = "Composition")
beta_ref_pred <- get_time_predictions(beta_ref_model, 
                                      beta_diversity_reference)
structure_ref_pred <- get_time_predictions(structure_ref_model, 
                                           structure_reference)
beta_ref_pred$Metrics <- "Beta diversity"
beta_ref_pred$Comparison <- "Restored vs Reference"
structure_ref_pred$Metrics <- "Community structure"
structure_ref_pred$Comparison <- "Restored vs Reference"
composition_time_predictions_ref <- rbind(
  beta_ref_pred, structure_ref_pred
)%>% mutate(Parameter = "Composition")


composition_raw_degraded_time <- composition_raw_degraded %>%
  mutate(Parameter = "Alpha diversity") %>%
  select(yi, vi, Restoration_time, Metrics, Comparison, Parameter)


composition_raw_ref_time <- composition_raw_reference %>%
  mutate(Parameter = "Alpha diversity") %>%
  select(yi, vi, Restoration_time, Metrics, Comparison, Parameter)
```

```{r, eval = FALSE}
composition_time_ppt_1 <- ggplot(composition_time_predictions_deg, aes(x = Restoration_time, 
                                           y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = composition_raw_degraded_time, aes(y = yi), 
             alpha = 0.3, size = 1.5, 
             shape = 21, color = "grey30", 
             fill = "orange") +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.3, 
              fill = "grey") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(
    x = "Restoration time (Yrs)",
    y = "lnRR (Composition)"
  ) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()
  ) +
  facet_wrap(~Metrics, scales = "free", ncol = 4)

composition_time_ppt_1

composition_time_ppt_2 <- ggplot(composition_time_predictions_ref, aes(x = Restoration_time, 
                                           y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = composition_raw_ref_time, aes(y = yi), 
             alpha = 0.3, size = 1.5, 
             shape = 1, color = "grey30", 
             fill = "white") +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.3, 
              fill = "darkgreen") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(title = "Restored vs Reference",
    x = "Restoration time (Yrs)",
    y = "lnRR"
  ) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()
  ) +
  facet_wrap(~Metrics, scales = "free", ncol = 4)

composition_time_ppt_2
```

## Relative abundance

```{r, eval = FALSE}
Asco_restoration_deg_model <- rma.mv(yi, vi, 
                                     mods = ~ Restoration_time, 
                                     random = ~ 1 | ID, 
                                     data = a_Ascomycota_degraded)
Asco_restoration_deg_model
Asco_restoration_ref_model <- rma.mv(yi, vi, 
                                     mods = ~ Restoration_time , 
                                     random = ~ 1 | ID, 
                                     data = a_Ascomycota_reference)
Asco_restoration_ref_model
Basidio_restoration_deg_model <- rma.mv(yi, vi, 
                                        mods = ~ Restoration_time , 
                                        random = ~ 1 | ID, 
                                        data = a_Basidiomycota_degraded)
Basidio_restoration_deg_model
Basidio_restoration_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_time , 
                                        random = ~ 1 | ID, 
                                        data = a_Basidiomycota_reference)
Basidio_restoration_ref_model
Ascomycota_deg_pred <- get_time_predictions(Asco_restoration_deg_model, 
                                            a_Ascomycota_degraded)
Basidiomycota_deg_pred <- get_time_predictions(Basidio_restoration_deg_model, 
                                               a_Basidiomycota_degraded)
Ascomycota_ref_pred <- get_time_predictions(Asco_restoration_ref_model, 
                                            a_Ascomycota_reference)
Basidiomycota_ref_pred <- get_time_predictions(Basidio_restoration_ref_model, 
                                               a_Basidiomycota_reference)
Ascomycota_deg_pred$Metrics <- "Ascomycota"
Ascomycota_deg_pred$Comparison <- "Restored vs Degraded"
Ascomycota_ref_pred$Metrics <- "Ascomycota"
Ascomycota_ref_pred$Comparison <- "Restored vs Reference"
Basidiomycota_deg_pred$Metrics <- "Basidiomycota"
Basidiomycota_deg_pred$Comparison <- "Restored vs Degraded"
Basidiomycota_ref_pred$Metrics <- "Basidiomycota"
Basidiomycota_ref_pred$Comparison <- "Restored vs Reference"
abundance_time_predictions_deg <- rbind(
  Ascomycota_deg_pred, Basidiomycota_deg_pred
)%>% mutate(Parameter = "Relative abundance")
abundance_time_predictions_ref <- rbind(
  Ascomycota_ref_pred, Basidiomycota_ref_pred
)%>% mutate(Parameter = "Relative abundance")


Ascomycota_Basidiomycota_deg_raw_time <- Ascomycota_Basidiomycota_deg_raw %>%
  mutate(Parameter = "Alpha diversity") %>%
  select(yi, vi, Restoration_time, Metrics, Comparison, Parameter)


Ascomycota_Basidiomycota_ref_raw_time <- Ascomycota_Basidiomycota_ref_raw %>%
  mutate(Parameter = "Alpha diversity") %>%
  select(yi, vi, Restoration_time, Metrics, Comparison, Parameter)

```

```{r, eval = FALSE}
abundance_time_predictions_deg
abundance_time_predictions_ref

Ascomycota_Basidiomycota_deg_raw_time

abundance_time_ppt_1 <- ggplot(abundance_time_predictions_deg, aes(x = Restoration_time, 
                                           y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = Ascomycota_Basidiomycota_deg_raw_time, aes(y = yi), 
             alpha = 0.3, size = 1.5, 
             shape = 21, color = "grey30", 
             fill = "orange") +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.3, 
              fill = "grey") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(
    x = "Restoration time (Yrs)",
    y = "lnRR (Relative abundance)"
  ) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()
  ) +
  facet_wrap(~Metrics, scales = "free", ncol = 4)

abundance_time_ppt_1

abundance_time_ppt_2 <- ggplot(abundance_time_predictions_ref, aes(x = Restoration_time, 
                                           y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = Ascomycota_Basidiomycota_ref_raw_time, aes(y = yi), 
             alpha = 0.3, size = 1.5, 
             shape = 1, color = "grey30", 
             fill = "white") +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.3, 
              fill = "darkgreen") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(title = "Restored vs Reference",
    x = "Restoration time (Yrs)",
    y = "lnRR"
  ) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()
  ) +
  facet_wrap(~Metrics, scales = "free", ncol = 4)

abundance_time_ppt_2
```

## Biomass

```{r, eval = FALSE}
plfa_deg_model <- rma.mv(yi, vi, mods = ~ Restoration_time, 
                         random = ~ 1 | ID, data = a_PLFA_degraded)
plfa_deg_model
plfa_ref_model <- rma.mv(yi, vi, mods = ~ Restoration_time , 
                         random = ~ 1 | ID, data = a_PLFA_reference)
plfa_ref_model
get_time_predictions <- function(model, dataset) {
  time_seq <- seq(min(dataset$Restoration_time), 
                  max(dataset$Restoration_time), length.out = 50)
  pred <- predict(model, newmods = time_seq)
  
  data.frame(
    Restoration_time = time_seq,
    pred = pred$pred,
    ci.lb = pred$ci.lb,
    ci.ub = pred$ci.ub
  )
}
plfa_deg_pred <- get_time_predictions(plfa_deg_model, a_PLFA_degraded)
plfa_ref_pred <- get_time_predictions(plfa_ref_model, a_PLFA_reference)
plfa_deg_pred$Metrics <- "PLFA content"
plfa_deg_pred$Comparison <- "Restored vs Degraded"
plfa_ref_pred$Metrics <- "PLFA content"
plfa_ref_pred$Comparison <- "Restored vs Degraded"
plfa_deg_pred%>% mutate(Parameter = "Biomass")
plfa_ref_pred%>% mutate(Parameter = "Biomass")


a_PLFA_reference_time <- a_PLFA_reference %>%
  mutate(Parameter = "Alpha diversity") %>%
  select(yi, vi, Restoration_time, Metrics, Comparison, Parameter)

a_PLFA_degraded_time <- a_PLFA_degraded %>%
  mutate(Parameter = "Alpha diversity") %>%
  select(yi, vi, Restoration_time, Metrics, Comparison, Parameter)
```

```{r, eval = FALSE}
plfa_time_ppt_1 <- ggplot(plfa_deg_pred, aes(x = Restoration_time, 
                                           y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = a_PLFA_degraded_time, aes(y = yi), 
             alpha = 0.3, size = 1.5, 
             shape = 21, color = "grey30", 
             fill = "orange") +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.3, 
              fill = "grey") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(
    x = "Restoration time (Yrs)",
    y = "lnRR (Biomass)"
  ) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()
  ) +
  facet_wrap(~Metrics)

plfa_time_ppt_1

plfa_time_ppt_2 <- ggplot(plfa_ref_pred, aes(x = Restoration_time, 
                                           y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = a_PLFA_reference_time, aes(y = yi), 
             alpha = 0.3, size = 1.5, 
             shape = 1, color = "grey30", 
             fill = "white") +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.3, 
              fill = "darkgreen") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(title = "Restored vs Reference",
    x = "Restoration time (Yrs)",
    y = "lnRR"
  ) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "plain"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank()
  ) +
  facet_wrap(~Metrics)

plfa_time_ppt_2
```

## Figure 4

```{r, eval = FALSE}


composition_raw_degraded_time <- composition_raw_degraded_time %>%
  mutate(Metrics = recode(Metrics, "Structure" = "Community structure"))

time_raw <- rbind(alpha_diversity_deg_raw_time,
                  composition_raw_degraded_time,
                  Ascomycota_Basidiomycota_deg_raw_time,
                  a_PLFA_degraded_time)%>%slice(-408)
time_raw$Metrics <- factor(time_raw$Metrics, 
                           levels = c("Observed richness", 
                                      "Chao1 richness",
                                      "Shannon index",
                                      "Simpson index",
                                      "Ascomycota", 
                                      "Basidiomycota",
                                      "Beta diversity", 
                                      "Community structure",
                                      "PLFA content"))
time_combined_deg <- bind_rows(alpha_time_predictions_deg, 
                               composition_time_predictions_deg, 
                               abundance_time_predictions_deg, 
                               plfa_deg_pred)


time_combined_deg$Metrics <- factor(time_combined_deg$Metrics, 
                                    levels = c("Observed richness", 
                                               "Chao1 richness",
                                               "Shannon index",
                                               "Simpson index",
                                               "Ascomycota", 
                                               "Basidiomycota",
                                               "Beta diversity",
                                               "Community structure",
                                               "PLFA content"))
time_plot <- ggplot(time_combined_deg, aes(x = Restoration_time, 
                                           y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = time_raw, aes(y = yi), 
             alpha = 0.5, size = 3, 
             shape = 21, 
             fill = "orange",
            color = "black",
            stroke = 0.2) +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.6, 
              fill = "grey60") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(title = "Restored vs Degraded",
    x = "Restoration time (Yrs)",
    y = "lnRR"
  ) +
  theme_bw(base_size = 12) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    strip.background = element_rect(fill = "grey95"),
    strip.text = element_text(size = 14),
    axis.text = element_text(size = 13),
    axis.text.x = element_text(size = 16),
    axis.title = element_text(size = 16)  # Add this for both axis titles
  ) +
  facet_wrap(~Metrics, scales = "free")

time_plot
 
```

```{r, eval = FALSE}
ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/restoration_time/figure_4.1.jpg",
       time_plot, dpi = 600, height = 9, width = 8)
```

```{r, eval = FALSE}

composition_raw_ref_time <- composition_raw_ref_time %>%
  mutate(Metrics = recode(Metrics, "Structure" = "Community structure"))



time_ref_raw <- rbind(alpha_diversity_ref_raw_time,
                      composition_raw_ref_time,
                      Ascomycota_Basidiomycota_ref_raw_time,
                      a_PLFA_reference_time)
time_ref_raw$Metrics <- factor(time_ref_raw$Metrics, 
                               levels = c("Observed richness", 
                                          "Chao1 richness",
                                          "Shannon index", 
                                          "Simpson index", 
                                          "Ascomycota", 
                                          "Basidiomycota",
                                          "Beta diversity", 
                                          "Community structure",
                                          "PLFA content"))
time_combined_ref <- bind_rows(alpha_time_predictions_ref, 
                               composition_time_predictions_ref, 
                               abundance_time_predictions_ref, 
                               plfa_ref_pred)
time_combined_ref$Metrics <- factor(time_combined_ref$Metrics, 
                                    levels = c("Observed richness", 
                                               "Chao1 richness",
                                               "Shannon index", 
                                               "Simpson index", 
                                               "Ascomycota", 
                                               "Basidiomycota",
                                               "Beta diversity", 
                                               "Community structure",
                                               "PLFA content"))
time_plot1 <- ggplot(time_combined_ref, aes(x = Restoration_time, y = pred)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_point(data = time_ref_raw, aes(y = yi), 
             alpha = 0.5, size = 3, shape = 21 ,
             fill = "cyan3",
            color = "black",
            stroke = 0.2) +
  geom_ribbon(aes(ymin = ci.lb, ymax = ci.ub), alpha = 0.5, 
              fill = "grey60") +
  geom_line(color = "black", linewidth = 0.5) +
  labs(title ="Restored vs Reference",
    x = "Restoration time (Yrs)",
    y = "lnRR"
  ) +
  theme_bw(base_size = 12) +
  theme(
    
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    strip.background = element_rect(fill = "grey95"),
    strip.text = element_text(size = 14),
    axis.text = element_text(size = 13),
    axis.text.x = element_text(size = 16),
    axis.title = element_text(size = 16)
  ) +
  facet_wrap(~Metrics, scales = "free")
time_plot1
```

```{r, eval = FALSE}
ggsave("Article_25_Meta-analysis/Meta_analysis/R/Data/Data_sorting/Figure/restoration_time/figure_4.2.jpg",
       time_plot1, dpi = 600, height = 9, width = 8)
```
